# Introduction


## Basic Information

This assessment reports the status of `r spp` (*`r spp_latin`*) off the `r state` coast using data through `r endyr`. 

The stock off the `r state` coast was assessed as a separate stock from other populations off the U.S. West Coast based on the fairly sedentary nature of `r spp` [@HannahandRankin_rockfish_site_fidelity_2011; @tolimieri_home_2009], which likely limits movement of fish between Oregon and California and Oregon and Washington. The substrate of the southern Washington coast is typically sandy bottom, a poor substrate for `r spp`, which creates a natural separation between the Oregon and Washington populations. Additionally, the exploitation history and magnitude of removals off the `r state` coast differ from those in Washington and California.    

<!-- Life history -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '1_introduction_basic_life_ecosystem.Rmd')
read_child(filein)
```

## Historical and Current Fishery Information

`r Spp` off the coast of `r state` is caught in both the commercial and recreational fisheries (Table \ref{tab:allcatches} and Figure \ref{fig:catch}). The reported landings from the commercial fishery extend back to 1892 and, other than a small peak in the late 1930s through the 1940s, were minimal until the late-1960s. Currently, `r spp` is one of several rockfish species targeted by a nearshore, primarily live-fish, fixed-gear fishery centered on `r state`'s southern coast. Following the development of the nearshore commercial fishery in the late 1990s, Oregon Department of Fish and Wildlife (ODFW) implemented a state-permitted limited access fishery that regulated fleet size, period landing limits, and established harvest guidelines [@rodomsky_2019_2020]. `r Spp` is one of 11 species in the Other Nearshore Rockfish category managed under a single state harvest guideline. Within this management category, China, quillback, and copper rockfish are the three primary species landed. Data on landings from the recreational fishery off the coast of `r state` began in 1979 and removals from the recreational fleet have increased across time and now represent the majority of landings for `r spp` off the coast of `r state`. Recreational landings were large in the year that data were first available, and were expected to be minimal prior to the 1970s. Consequently a linear ramp in recreational landings was applied from 1970 to 1979.


<!-- Summary of Management History and Performance -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '1_introduction_management.Rmd')
read_child(filein)
```

The current OFL contribution and implied ACL contribution for `r spp` North of 40$^\circ$ 10' Lat. N., the state specific ACL allocation (58.4% for `r state`; Groundfish Management Team, pers. comm.), and the total removals are shown in Table \ref{tab:ofl}.