\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

<!-- tab:catch -->
\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/Catches_All_Years.tex}

\newpage


```{r, results = 'asis'}
yrs = hist = 2011:2020
nfleets = 2
catch = dead = total.dead = 0
for (i in 1:nfleets){
  name = paste0("retain(B):_",i)
  input.catch = model$timeseries[model$timeseries$Yr %in% yrs, name]
  catch = cbind(catch, input.catch)
}
total.catch <- round(apply(catch, 1, sum),2)

man = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")
man = man[man$Year %in% yrs, ]
out = cbind(round(man,2), round(man$ACL * 0.584, 2), total.catch)

col_names = c("Year", "OFL", "ACL", "OR ACL", "OR Removals")

table_format(x = out,
             caption = "The OFL and ACL for quillback rockfish within the Minor Nearshore Rockfish North complex, the ACL allocated to Oregon, and the total removals.",
             label = "ofl",
             align = 'l',
             col_names = col_names)


```

\newpage


<!-- ======================================================= -->
<!-- ***************       Data      *********************** --> 
<!-- ======================================================= -->


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/OR_Samples_Feb2021.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/or_rec_samples.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/len_at_weight_data.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/len_at_age_data.tex}

\newpage


<!-- \input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/or_rec_age_samples.tex} -->

<!-- \newpage -->


<!-- \input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/OR_age_Samples_Feb2021.tex} -->

<!-- \newpage -->

<!-- ======================================================= -->
<!-- ***************    Biology      *********************** --> 
<!-- ======================================================= -->

```{r, results='asis'}

growth = model$endgrowth[model$endgrowth$Sex == 1, ]
out = growth[, c("Age_Beg", "Len_Beg", "Wt_Beg", "Len_Mat", "Mat*Fecund")]
out$Len_Mat[out$Len_Mat > 0.99] = 1
rownames(out) = NULL
col_names = c('Age', 'Length (cm)', 'Weight (kg)', 'Maturity', 'Spawning Output')

table_format(x = out[1:51,],
             caption = "Age, length, weight, maturity, and spawning output by age (product of maturity and fecundity) at the start of the year. Output for ages 51-95 is truncated as these ages have the same length, weight, maturity, and spawning output as at age 50.",
             label = "growth-tab",
             digits = c(0, 2, 2, 2, 2),
             align = 'l',
             col_names = col_names,
             longtable = TRUE) 

```

\newpage

<!-- ======================================================= -->
<!-- ***************  Data Weights   *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'data_weights.csv'))

col_names = c('Method',
        'Commercial Lengths',
              'Recreational Lengths')
table_format(x = tab,
             caption = "Data weights applied by each alternative data weighting method. The Dirichlet Multinomial weight is theta/(1+theta)",
             label = "dw",
             align = 'l',
             col_names = col_names)
```

<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}

mod_params = model$parameters[-c(grep('Impl',model$parameters$Label),
							     grep('Fore',model$parameters$Label)),
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 

mod_params[model$parameters$Label=="NatM_p_1_Fem_GP_1","Pr_SD"] = 0.438 #update for model 800

test = mod_params[which(mod_params$Label == "Wtlen_1_Fem_GP_1"),'Value']
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 

# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')

# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))

# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Fem_GP_1",3]), 3)

# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])

#Reformat so can show a value for alpha in length-weight relationship
mod_params[,"Value"] = format(mod_params$Value, digits = 2)
mod_params[which(mod_params$Label == "Wtlen 1 Fem GP 1"), "Value"] = test

# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')

table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("6cm", "4cm"))                         

```
<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

<!-- tab:likes -->
\include{tex_tables/likelihoods.tex}


<!-- ======================================================= -->
<!-- ***********    Reference Points  ******************** --> 
<!-- ======================================================= -->

<!-- tab:referenceES -->
```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "e_ReferencePoints_ES.csv"))
tab = tab[-13,]
col_names = c("", "Estimate", "Lower Interval", "Upper Interval")

tab$Estimate = round(suppressWarnings(as.numeric(tab$Estimate)),2)
tab$Estimate[is.na(tab$Estimate)] = "-"

tab$Lower.Interval = round(suppressWarnings(as.numeric(tab$Lower.Interval)),2)
tab$Lower.Interval[is.na(tab$Lower.Interval)] = "-"

tab$Upper.Interval = round(suppressWarnings(as.numeric(tab$Upper.Interval)),2)
tab$Upper.Interval[is.na(tab$Upper.Interval)] = "-"

table_format(x = data.frame(tab),
                 caption = "Summary of reference points and management quantities, including estimates of
the 95 percent intervals.",
                 label = "referenceES",
                 longtable = TRUE,
                 col_names = col_names,
                 align = c('r','c', 'c', 'c'),
                 row.names = FALSE)

#kableExtra::save_kable(t, file = file.path("C:/Users/Brian.Langseth/Desktop/or/tex_tables", 
#                                           paste0("e_ReferencePoints_ES", ".tex")))
```

<!-- \input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/e_ReferencePoints_ES.tex} -->

\newpage


<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

<!-- tab:timeseries -->
```{r, results = 'asis'}
timeseries = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/or/8_0_0_postSSC_base", "tables", "TimeSeries.csv"))
col_names = c("Year", "Total Biomass (mt)", "Spawning Output", "Total Biomass 3+ (mt)", "Fraction Unfished", "Age-0 Recruits", "Total Mortality (mt)", "1-SPR", "Exploitation Rate")

table_format(x = round(timeseries,2),
                 caption = "Time series of population estimates from the base model.",
                 label = "timeseries",
                 longtable = TRUE,
                 col_names = col_names,
                 row.names = FALSE)
```
<!-- \input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/TimeSeries.tex} -->

\newpage


<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->

<!-- tab:sensitivities -->
\include{tex_tables/sensitivities_updated.tex}

\newpage

<!-- ======================================================= -->
<!-- ****************         SSS            *************** --> 
<!-- ======================================================= -->

<!-- \input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/sss_40.tex} -->

<!-- \newpage -->

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
tab = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/or/8_0_0_postSSC_base", 'tables', 'g_Projections_ES.csv'))
man = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")

out = cbind(tab$Year,
            c(round(man[man$Year %in% c(2021, 2022), "OFL"],2), rep("-",10)),
            c(round(man[man$Year %in% c(2021, 2022), "ACL"],2), rep("-",10)),
            c(round(man[man$Year %in% c(2021, 2022), "ACL"] * 0.584,2), rep("-", 10)),
            c(round(tab[1:2,3],2), rep("-",10)),
            c(rep("-",2), round(tab[3:12,2], 2)),
            c(rep("-",2), PEPtools::get_buffer(2021:2032,1,0.45)[-c(1,2),2]),
            c(rep("-",2), round(round(tab[3:12,2],3)*PEPtools::get_buffer(2021:2032,1,0.45)[-c(1,2),2],2)),  
            c(rep("-",2), round(tab[3:12,3],2)),
            #c(rep("-",2), round(tab[3:12,3]/tab[3:12,2], 3)),
            round(tab[ ,5:ncol(tab)], 2))

col_names = c('Year',
              'OFL North',
              'ACL North',
              "OR ACL North",
              "Assumed removals",
              "OFL",
              "Buffer",
              "ABC", 
              "ACL",
              "Spawning Output",
              "Fraction Unfished")
table_format(x = out,
             caption = "Projections of potential OFLs (mt), ABCs (mt), resulting ACLs (mt) based on 40-10 rule, estimated spawning output, and fraction unfished for 2023-2032, with assumed removals in 2021 and 2022 based on the average total mortality from 2017-2020. The OFL North and ACL North for 2021 and 2022 reflect adopted management limits for quillback rockfish for the area north of 40.10 Latitude N, while the OR ACL North is the Oregon specific allocation of the total ACL.",
             label = "project",
             align = 'l',
             col_names = col_names,
             landscape = FALSE)
```

\newpage

```{r, results = 'asis'}
tab = read.csv(file.path("C:/Users/Brian.Langseth/Desktop", "or", "decision_tables", "decision_table_OR_R0_baseABC.csv"), header = TRUE)

col_names = c("Year", 
              "Catch (mt)", 
              "Low: Spawning Output", 
              "Low: Fraction Unfished", 
              "Base: Spawning Output", 
              "Base: Fraction Unfished", 
              "High: Spawning Output", 
              "High: Fraction Unfished")

table_format(x = tab,
             caption = "Decision table for low (2.01) and high (2.28) states of nature around ln(R0).",
             label = "decision-table",
             align = 'l',
             col_names = col_names,
             landscape = FALSE)
```

\newpage


