---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
preamble: |
output: sa4ss::techreport_pdf
bibliography: sa4ss.bib
lang: en
papersize: a4
---

```{r opts, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)  
        }
  })

load("00opts.Rdata")

spp = 'quillback rockfish'
Spp = 'Quillback rockfish'
spp_latin = 'Sebastes maliger'
state = 'Oregon'

data_fig_loc = "//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/output biology/plots"

if(file.exists("00mod.Rdata")){
  load("00mod.Rdata")
} else {
  print("Model output not being read. Please run the read_model() function.")
}

```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: Brian J. Langseth
    code: 1
    first: B
    middle: J
    family: Langseth
  - name: Chantel R. Wetzel
    code: 1
    first: C
    middle: R
    family: Wetzel
  - name: Jason M. Cope
    code: 1
    first: J
    middle: M
    family: Cope
  - name: Alison D. Whitman
    code: 2
    first: A
    middle: D
    family: Whitman
author_list: Langseth, B.J., C.R. Wetzel, J.M. Cope, A.D. Whitman
affiliation:
  - code: 1
    address: Northwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 2725
      Montlake Boulevard East, Seattle, Washington 98112
  - code: 2
    address: Oregon Department of Fish and Wildlife, 2040 Southeast Marine Science
      Drive, Newport, Oregon 97365
address:
  - ^1^Northwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 2725 Montlake
    Boulevard East, Seattle, Washington 98112
  - ^2^Oregon Department of Fish and Wildlife, 2040 Southeast Marine Science Drive,
    Newport, Oregon 97365
---

<!--chapter:end:00authors.Rmd-->

---
title: Status of Quillback Rockfish (_Sebastes maliger_) in U.S. waters off the coast of Oregon in 2021 using catch and length data
---

<!--chapter:end:00title.Rmd-->

\vspace{20cm}

_These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited (or reproduced). They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce._

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}

\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:01a.Rmd-->

\vspace{40cm}

_These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited (or reproduced). They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce._

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thetable}{\arabic{table}}
\renewcommand{\thefigure}{\arabic{figure}}
\setcounter{table}{0}
\setcounter{figure}{0}

\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:10a.Rmd-->

# Introduction


## Basic Information

This assessment reports the status of `r spp` (*`r spp_latin`*) off the `r state` coast using data through `r endyr`. 

The stock off the `r state` coast was assessed as a separate stock from other populations off the U.S. West Coast based on the fairly sedentary nature of `r spp` [@HannahandRankin_rockfish_site_fidelity_2011; @tolimieri_home_2009] which likely limits flow of fish between Oregon and California and Oregon and Washington. The substrate of the southern Washington coast is typically sandy bottom, a poor substrate for `r spp`, which creates a natural separation between the Oregon and Washington populations. Additionally, the exploitation history and magnitude of removals off the `r state` coast differ from those in Washington and California.    

<!-- Life history -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '1_introduction_basic_life_ecosystem.Rmd')
read_child(filein)
```

## Historical and Current Fishery Information

`r Spp` off the coast of `r state` is caught in both the commercial and recreational fisheries (Table \ref{tab:catch} and Figure \ref{fig:catch}). The reported landings from the commercial fishery extend back to 1892 and other than a small peak in the late 1930s through the 1940s, were minimal until the late-1960s. Currently, `r spp` is one of several rockfish species targeted by a nearshore, primarily live-fish, fixed-gear fishery centered on `r state`'s southern coast. Following the development of the nearshore commercial fishery in the late 1990s, ODFW implemented a state-permitted limited access fishery that regulated fleet size, period landing limits, and established harvest guidelines [@rodomsky_2019_2020]. `r Spp` is one of 11 species in the Other Nearshore Rockfish category managed under a single state harvest guideline. Within this management category, China, quillback, and copper rockfish are the three primary species landed. Landings from the recreational fishery off the coast of `r state` began in 1979 and removals from the recreational fleet have increased across time and now represent the majority of landings for `r spp` off the coast of `r state`. Recreational landings were large in the year that data were first available, and were expected to be minimal prior to the 1970s. Consequently a linear ramp in recreational landings was applied from 1970 to 1979.


<!-- Summary of Management History and Performance -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '1_introduction_management.Rmd')
read_child(filein)
```


<!--chapter:end:11introduction.Rmd-->

# Data
The following types and sources of data were used in this assessment. Fishery catch and composition data were specific to `r state`, however biological data were estimated coastwide and included Oregon, Washington, and California sources. 

1. Commercial landings, and length, weight, and age data obtained from PacFIN and the Oregon Department of Fish and Wildlife (ODFW). Age compositions were not fit directly in the model, but age data was used to estimate growth which were fixed inputs to the model. 
2. Estimates of commercial discard length frequencies and fraction discarded in the fishery obtained from the West Coast Groundfish Observer Program (WCGOP).
3. Recreational landings, discards, and length, weight, and age data obtained from RecFIN and the Oregon Department of Fish and Wildlife (ODFW). Age compositions were not fit directly in the model, but age data was used to estimate growth which were fixed inputs to the model. 
4. Fishery independent biological data (length, weight, and age) from the NWFSC WCGBTS survey.
5. Estimates of fecundity, maturity, and mortality from various sources.

A description of each data type is provided below, with timing of catch and composition data used in the base model shown in (Figure \ref{fig:data-plot}).

<!--chapter:end:20data.Rmd-->

## Fishery-Dependent Data

### Commercial Fishery

#### Landings

Historical commercial landings from 1892 to 1986 were provided by ODFW (Karnowski et al. 2014).  Historical landings were consistent but minimal (< 1 mt in all years except 1943) until the mid-1960s, at which point landings increased to a high of 3.5 mt in 1978. Primary gear types during this historical period included longline and troll gears. However, ODFW commercial samplers suggest that these troll landings were primarily landed on hook and line gear, but not separated by gear type on the fish tickets (pers. comm. M. Freeman, ODFW). 

Landings from 1987 – 1999 were compiled from a combination of PacFIN, which is the central repository for West coast commercial landings (extracted on 10/13/2020), and a separate ODFW reconstruction that delineated species-specific landings in the unspecified categories on PacFIN (e.g. URCK and POP1, ODFW 2017). `r Spp` landings from this reconstruction were substituted for the URCK and POP1 landings available from PacFIN, and added to PacFIN landings from other categories for a complete time series during this time period. Commercial landings from 2000 – 2020 are available on PacFIN (extracted on 10/13/2020 and 02/18/2021). `r Spp` is one of several rockfish species targeted by a nearshore, primarily live-fish fixed gear-fishery centered on Oregon’s southern coast. `r Spp` have been landed primarily with hook and line gear, though a substantial portion have been landed with bottom longline gear as well. Overall, 94.2% of `r spp` landings are from these two gear types (2000 – 2020). In the most recent years, longline landings have eclipsed hook and line landings. Landings from other gear types, including fish pot and trawl, are minimal relative to hook and line and longline gears and are sporadic. Commercial landings for `r spp` increased from the mid-1960s to 1974 and have since fluctuated between approximately 0.4 and 4.5 mt annually. From 2003 to 2020, landings have averaged 1.6 mt annually, and represent approximately one third of the total removals. Commercial landings were aggregated across gear types into a single fleet for the base model. 

[Discuss possible questions about differences in selectivity between the gears]

The input catches in the model represent total removals: landings plus discards (Table \ref{tab:catch} and Figure \ref{fig:catch}). Discards totals for the commercial fleet from 2002-2019 were determined based on West Coast Groundfish Observer Program (WCGOP) data provided in the Groundfish Expanded Mortality Multiyear (GEMM) product. The total coastwide observed discards in trawl and fixed gears were allocated by state and area based on the total observed landings observed by WCGOP. Discards were added to landings to obtain total removals for 2002-2019. Total removals prior to 2002, and for 2020 where no WCGOP data were yet available, were calculated based on the average discard rates of fixed gears from WCGOP for `r state` (5.7 percent). A fixed gear discard rate was used to better match the historical fleet as trawl catches and therefore discards were higher in the 2000s but lower before the 2000s.  

#### Length Compositions

Commercial `r spp` length samples are available from PacFIN from 1998 – 2020 (Table \ref{tab:com-len-samps}, extracted 2/23/2021). Approximately 44.3% of these samples are females (n = 1,361) and 54.2% are males (n = 1,664). There were 46 unsexed fish. The majority (77.2%) are from the southern Oregon coast, centered in Port Orford (65.3%) and Gold Beach (11.9%), where the majority of permit holders for the commercial nearshore fishery are based and where most of the landings are made. The majority of length samples are from `r spp` landed live (57.4%). Additionally, special projects length samples collected from the commercial fishery are available from PacFIN from 1999 – 2001, 2003 – 2006, 2008, 2010, 2012, 2015, and 2017 – 2019 (n = 210; extracted on 12/11/2020), but were not used due to concerns over non-random sampling.  

The distribution of the lengths in the commercial data ranged between 21 - 54 cm (the maximum length data bin size, Figure \ref{fig:com-len-data}). The mean size observed by the commercial fishery was relatively variable from year to year with the mean length occuring between 35 - 41 cm for all but the first two years, where mean length was 27 and 29 cm (Figure \ref{fig:mean-com-len-data}). 

The length observations in 1998 were not used in the base model due to very low (four) annual sample size. These data were used in the model as a 'ghost' fleet, not fit by the model but implied fits reflected in diagnostic output. The implied fit to these data from the base model are shown in [Appendix A](#append_a). 

The input sample sizes for the commercial length data were calculated via the Stewart method (Ian Stewart, personal communication) which incorporate the number of trips and fish by year:

\begin{centering}

Input effN = $N_{\text{trips}} + 0.138 * N_{\text{fish}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $<$ 44

Input effN = $7.06 * N_{\text{trips}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $\geq$ 44

\end{centering}

[Describe that these were expnaded comps - and describe process]


### Recreational Fishery

#### Landings

_Historic Ocean Boat Landings (1979 – 2000)_

Recently, the Oregon Department of Fish and Wildlife (ODFW) undertook an effort to comprehensively reconstruct all marine fish recreational ocean boat landings prior to 2001 (pers. comm. A. Whitman, ODFW). Reconstructed catch estimates from the Oregon Recreational Boat Survey (ORBS) improve upon estimates from the federal Marine Recreational Fisheries Statistical Survey (MRFSS), which have known biases related to effort estimation and sampling [@van_voorhees_evaluation_2000] that resulted in catch estimates considered implausible by ODFW. However, the ORBS sample estimates are known to lack the comprehensive spatial and temporal coverage of MRFSS. Addressing this coverage issue is a major part of this reconstruction. In general, the base data and methodology for these reconstructed estimates are consistent with recent assessments for other nearshore species [@dick_china_2016; @dick_bluedeacon_2018; @haltuch_lingcod_2018; @cope_cabezon_2019]. 

Prior to 2001, ORBS monitored marine species in both multi-species categories, such as rockfish, flatfish, and other miscellaneous fishes, and as individual species, such as lingcod or halibut. For this comprehensive reconstruction, four species categories were selected to reconstruct, including rockfish, lingcod, flatfish and miscellaneous, which constitute the bulk of the managed marine fish species. `r Spp` are a component of the rockfish species category. 

Category-level estimates were expanded to account for gaps in sampling coverage in two separate pathways. First, estimates from five major ports were expanded to include unsampled winter months in years lacking complete coverage. Expansions were based on available year-round sampling data and excluded years where regulations may have impacted the temporal distribution of catch.  Second, all other minor port estimates were expanded to include seasonal estimates in years lacking any sampling based on the amount of minor port catch as compared to all major port estimates. A subset of landings were sampled by ORBS for species compositions within these categories. Once category-level landings were comprehensive in space and time, species compositions were applied for the three multi-species categories, including rockfish, flatfish and miscellaneous fish. Borrowing rules for species compositions were specific to the category and determined based on a series of regression tree analyses that detailed the importance of each domain (year, month, port and fishing mode) to variability in compositions. 

Ocean boat estimates from 1979 – 2000 in numbers of fish of `r spp` from the above described methods were converted to biomass using biological samples from MRFSS (pers. comm. A. Whitman, ODFW). MRFSS biological data are available from 1980 – 1989 and 1993 – 2000. An annual average weight was applied to the total annual number of fish to obtain an annual landings estimate. Several years missing biological data (1979, 1990 – 1992) were filled in using neighboring years or interpolation. These landings in biomass were provided by ODFW and do not include an estimate of discarded fish. Landings during this time period gradually increased from 1979 to a peak of 7.1 mt in 1992, but fluctuated annually. Recreational landings were large in 1979, the year that data were first available, and were expected to be minimal prior to the 1970s. Consequently a linear ramp in recreational landings was applied from 1970 to 1979 for this assessment.   

_Modern Ocean Boat Landings (2001 – 2020)_

Recreational landings for ocean boat modes from 2001 – 2020 are available from RecFIN.  Both retained and released estimates of mortality are included, though retained mortality contributes the vast majority to total mortality. Release mortality is estimated from angler-reported release rates and the application of discard mortality rates from the PFMC.  From 2001 – 2020, landings averaged 4.6mt, ranging from 0.7 to 9.5 mt. In 2020, ocean boat landings were 6.3 mt.

_Shore and Estuary Landings (1979 – 2020)_

ODFW provided reconstructed estimates of shore and estuary landings for `r spp` from 1979 – 2020, using methodology similar to recent assessments [@berger_kelpgreenling_2015, @dick_bluedeacon_2018, @cope_cabezon_2019]. Data sources include MRFSS and the Oregon Shore and Estuary Boat Survey (SEBS). Numbers of fish were provided by MRFSS from 1980 – 1989 and 1993 – June 2003, and by SEBS from July 2003 – June 2005. An annual mode-specific average weight was applied to numbers of `r spp` from 1980 – 1989 and 1993 – 2005. Separate weights were calculated for shore and estuary boat modes, and excluded extreme outliers and imputed values. This reconstruction also applied two scaling factors to remove bias towards freshwater sampling and underestimation of estuary boats, as detailed in [@dick_bluedeacon_2018]. To estimate `r spp` landings from July – December 2005, an expansion was developed using the three year average of the ratio between the first six months of the year and the total annual landings from MRFSS and SEBS landings from 2002 - 2004. Separate expansions were developed for shore mode and estuary boat modes. A three year average (1980 - 1982) was used to estimate shore and estuary boat landings for 1979.  

The ODFW does not currently sample shore and estuary boat fishing trips, and so a 10 year average landing (1996 – 2005; 0.024 mt/year) was used to estimate shore and estuary boat landings during 2006 – 2020. Shore and estuary boat landings for `r spp` were sporadic. Shore and estuary boat landings averaged 0.07 mt annually from 1980 – 2003.

Recreational removals were aggregated across modes into a single fleet in the model (Table \ref{tab:catch} and Figure \ref{fig:catch}). Values from 2001-2020 represent total removals consisting of both landings and estimated discard mortality. No recreational discarding was assumed for the years 2000 and prior, because the bag limits (15 fish bag limit) are thought to not have been restrictive enough to induce appreciable size based discarding of `r spp`.

#### Length Compositions

Recreational length samples were obtained from two sources: MRFSS and RecFIN (ORBS). From 1980 – 1989 and from 1993 – 2000, the MRFSS program collected samples from both ocean and inland (estuary) areas. ODFW provided MRFSS samples with the addition of a column that flagged length values imputed from weights to allow for selection of directly measured values; however, sample size was limited and therefore, imputed lengths were used.  From 1980 – 1989, total lengths (mm) were collected by MRFSS, which were converted to fork length. From 1993 – 2000, fork length (mm) was collected. Length samples from 2001 – 2020 from the ORBS sampling program are available on RecFIN. All ORBS samples are by fork length (mm). The vast majority (78%) of these samples are from ocean trips, or do not distinguish inland from ocean (21%). Special projects samples collected by ODFW staff from the recreational fishery are also available from 1998 – 2001 and 2013 - 2015 (n = 150), but were not used due to concerns about non-random sampling. Table \ref{tab:len-samps} details sample sizes used by year in the base model. Retention of `r spp` was not allowed under recreational state regulations in 2015 or 2016, limiting the number of samples in those years. Furthermore, released samples (n = 121), of which 60 occurred in 2015 and 2016, were not used in length compositions for the base model.   

The distribution of the lengths in the recreational data ranged between 20 - 54 cm (the maximum length data bin size, Figure \ref{fig:rec-len-data}). The mean length by year in the recreational data was more variable prior to 2000, after which the mean lengths observed by year became relatively stable with tight 95 percent confidence intervals (Figure \ref{fig:mean-rec-len-data}).

The input sample sizes for the recreational length data were calculated equal to the number of length samples available by year. 

<!--chapter:end:21f-.Rmd-->

## Fishery-Independent Data

No fishery-independent data sources that are commonly incorporated in West Coast groundfish assessments (as required by the data moderate Terms of Reference) had adequate sample size of `r spp` off the `r state` coast to include abundance indices for this assessment. The WCGBTS, and historically the Triennial survey, collect data off the `r state` coast on rockfish biology and abundance. There were no more than ten positive tows of `r spp` in any one year coastwide in the WCGBTS, but typically fewer than five. Similarly there were no more than five positive tows of `r spp` in any one year coastwide for the Triennial survey. Given indices of abundance were not calculated due to small sample sizes, length composition data from the WCGBTS (n = 102) and Triennial Survey (n = 5) off `r state` were not included in the model. Biological data from the WCGBTS survey was used in external calculations of biological parameters, including growth and weight-at-length relationships. No ages or weights for `r spp` were available from the Triennial survey. 

`r state` has a number of state-specific small-scale fishery-independent surveys considered by ODFW to have adequate samples of `r spp`. These include....

[need to add to this section]

Given these surveys are not commonly incorporated into West Coat groundfish assessments, and are not explicitly conducted as a state-wide estimate of relative or absolute abundance, we do not include the data in the model for `r spp`. However, we do compare estimates from these surveys to the our assessment model in Section \ref{unresolved-problems-and-major-uncertainties}.

[Update reference to section]

<!--chapter:end:21s-.Rmd-->

<!-- Biological Data -->
```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '2_biology.Rmd')
read_child(filein)
```

<!--chapter:end:22biology.Rmd-->

# Assessment Model

<!-- Summary of Previous Assessments and Bridging analysis -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_model_general.Rmd')
read_child(filein)
```


## Model Structure and Assumptions

`r coast` coast `r spp` was assessed using a one-sex model with life history parameters combined across sexes. The model assumed two fleets: 1) commercial and 2) recreational fleets with removals beginning in `r startyr`. Selectivity for the commercial fleet was specified to be asymptotic using the six-parameter double normal parameterization within Stock Synthesis. The ascending width and beginning size of maximum selectivity parameters were estimated for the commercial fleet. The selectivity for the recreational fleet was also specified using the six-parameter double normal parameterization with the ascending width and beginning size of maximum selectivity parameters estimated, and reduced selectivity for the largest fish was allowed (i.e., allowed to be dome-shaped). Annual recruitment deviations were estimated within the base model.

<!-- Modeling Platform and Structure and Priors and Data Weighting -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_model_details.Rmd')
read_child(filein)
```

<!-- Data Weighting -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_data_weighting.Rmd')
read_child(filein)
```

### Estimated and Fixed Parameters

There were `r tail(model$parameters$Active_Cnt,1)` estimated parameters in the base model. These included one parameter for $R_0$, 5 parameters for selectivity, 71 recruitment deviations, and 12 forecast recruitment deviations (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`, and natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)`, as described above in Section \ref{priors}. Growth, maturity-at-length, and length-at-weight were fixed as described above in Section \ref{biological-data}. The standard deviation of recruitment deviates was fixed at `r round(model$parameters[model$parameters$Label == "SR_sigmaR","Value"],2)`. Sensitivity analyses and likelihood profiles were performed for steepness, natural mortality, length at maximum size, and vonBertalanffy growth coefficient. 

Dome-shaped selectivity was explored for all fleets within the model. Older and larger `r spp` may be found in deeper waters and may move into areas that limit their availability to fishing gear as they mature. Dome shaped selectivity can also occur under heterogeneous fishing pressure across space by fleets [@Waterhouseetal_spatialSelex_2014].

The final base model estimated dome-shaped selectivity for the recreational fishery. The selectivty for the commercial fishery was fixed as asymptotic. During initial model development, the descending width and width of maximum selectivity parameters for the recreational and commercial fleets were estimated to identify appropriate fixed values consistent with the data, and then fixed at those estimates. 


## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the `r coast` coast. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.


<!--chapter:end:30model.Rmd-->

<!-- Base Model Results -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '33_results_basemodel.Rmd')
read_child(filein)
```

### Parameter Estimates

Estimated parameter values are provided in Table \ref{tab:params}. The $R_0$ was estimated at `r round(model$parameters[model$parameters$Label == 'SR_LN(R0)', 'Value'], 2)`. The selectivity curves for the commercial and recreational fleet are shown in Figure \ref{fig:selex}. The selectivity was fixed to be asymptotic for the commercial fleet with a peak in maximum selectivity for fish starting at `r round(model$parameters[model$parameters$Label == 'Size_DblN_peak_OR_Commercial(1)', 'Value'], 1)` cm. The selectivity for the recreational fleet was estimated to be dome-shaped at the largest sizes. The peak of the selectivity curve by the recreational fleet was estimated to start at `r round(model$parameters[model$parameters$Label == 'Size_DblN_peak_OR_Recreational(2)', 'Value'], 1)` cm and decline at 43 cm. Sensitivities to the shape and potential time blocking of the recreational selectivity was explored (see below in Section \ref{sensitivity-analyses}). After discussions with individuals knowledgable about the recreational fishery, we theorized that the dome-shape in selectivity could arise due to older and larger fish moving deeper and being unavailable to the recreational fishery, which often operates nearshore and often targets rockfish in the water column, such as black or blue/deacon rockfishes, rather than quillback rockfish, which is typically strongly associated with the bottom. Additionally, in most recent years, the recreational fishery has also been restricted to extreme nearshore waters (<20 – 40fm) to reduce impacts on overfished rockfishes, primarily yelloweye rockfish.

The estimated annual recruitment and recruitment deviations are shown in Figures \ref{fig:recruits} and \ref{fig:rec-devs}. Strong recruitment events were estimated to have occurred in 1993, 1995, 1999, and 2012 which resulted in a substantial increase in biomass during the late 1990s and early to mid 2000s. While the largest recruitment deviations were estimated to have occurred in these four specific years, the surrounding years in the 1990s also have above average recruitment estimated, whereas the surrounding years in the 2000s have lower than average recruitment estimated. Bias adjustment was applied to the annual estimates of recruitment deviations following the pattern of increased bias adjust for recent years as shown within r4ss (Figure \ref{fig:bias-adj}).

The large recruitment pulses in the 1990s show up in the composition data for the commercial and recreational fleets in some years as a pulse of young fish, but more so as a steady increasing trend in mean size that help contribute to the increasing catches over the time given the estimates of population size. The steadily increasing mean size in the recreational fleet along with minimal catches of smaller fish in the compositional data supports the below average recruitment in the 2000s, until 2012. The 2012 large recruitment pulses show up in the composition data for both the commercial and recreational fleets as pulses of smaller fish that are also reflected by declines in mean size. 

### Fits to the Data

Fits to the length data are shown based on the Pearson residuals-at-length, the annual mean lengths, and aggregated length composition data for the commercial and recreational fleets. The Pearson residuals for the commercial fishery have no discernible pattern of misfit to the length data across cohorts but show areas of misfit over time (Figure \ref{fig:com-pearson}). The residuals show that the peak of the composition is being underfit for many years. These years have lower sample size, and for years with high sample size such as 2000, 2002, and 2017, compositions are being fit well. The largest residuals were observed in 1999 or when missing small spikes of small fish in the compositions (2009, 2017, 2020) (see [Appendix A](#append_a) for details). The mean lengths observed by the commercial fishery were variable by year but with generally consistent confidence intervals across years and showed an increase in mean length followed by a period of stability and then decline (Figure \ref{fig:com-mean-len-fit}). 

The Pearson residuals for the recreational length data were variable by year and indicate no discernible pattern of misfit to the length data (Figure \ref{fig:rec-pearson}). A period of positive residuals from 2005-2014 show that the peak of the composition is being underfit, however looking at the fits suggest overall good fit (see [Appendix A](#append_a) for details). The residual patterns for 2017-2020, which are the largest residuals outside misfits to very high and very low lengths in low sample size years (before 1990), show the model has difficulty fitting the bimodal patterns in these years, which are not unexpected. Throughout the mid-2000s the mean length increases to a larger size (around 40 cm in 2015) with a substantial decrease in variation of the observed lengths compared to pre-2000 lengths (Figure \ref{fig:rec-mean-len-fit}). The mean length was highly variable in 2015 due to low sample size (Table \ref{tab:len-samps}) 

Aggregate fits by fleet are shown in Figure \ref{fig:agg-len-fit}. The model fits the aggregated lengths for the recreational fleet well. The fit to the commercial fleet is poorer. Both fleets show similar ranges of sizes caught and an aggregated peak around 40 cm. The commercial fleet shows proportionally less catch of intermediate size fish between 30-40 cm compared to the recreational fleet. The model overfits the proportion of intermediate fish in the commercial fishery and underestimates the proprotion of fish selected at their peak. Additional explorations with selectivity blocks for the commercial fleet did not greatly improve the aggregate fit. 

The poor fit to the commerical aggregate lengths was further explored by applying selectivity blocks to the commercial fleet, but fits to the aggregate fits generally remained unchanged. The differences on overall model results were small, and with lack of clear evidence for blocks within the commercial fleet, and added complexity with applying blocks, we chose not to include in the base model.

### Population Trajectory

The predicted spawning output (in millions of eggs) is given in Table \ref{tab:timeseries} and plotted in Figure \ref{fig:ssb}. The predicted spawning output from the base model declines until 1995, and steadies due to several above average recruitment events that occurred in the early- to mid-1990s. The population then increases dramatically in the early 2000s due to the very large recruitment event in 1995. The population increase slows in the late 2000s, and then declines in the 2010s due to below average recruitment through the 2000s. The estimate of total biomass over time is shown in Figure \ref{fig:tot-bio}.

The `r endyr` spawning output relative to unfished equilibrium spawning output is above the target of 40 percent of unfished spawning output (`r round(model$derived_quants[model$derived_quants$Label == 'Bratio_2021','Value'], 2)`, Figure \ref{fig:depl}). Approximate confidence intervals based on the asymptotic variance estimates show that the uncertainty in the estimated spawning output is large ranging between approximately 20 - 75 percent of unfished equilibrium spawning output. The standard deviation of the log of the spawning output in `r endyr` is `r round(model$Pstar_sigma, 2)`.

The slight dome shape in the final selectivity for the recreational fleet results in a fraction of large fish being unavailable in recent years (Figure \ref{fig:unavail-bio}). The fraction of large fish unavailable averaged five percent of the overall biomass since 1970, and in theory would be available for selection from the commercial fishery.  

The stock-recruit curve resulting from a value of steepness fixed at `r print(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)` is shown in Figure \ref{fig:bh-curve}. The estimated annual recruitment is shown in Figure \ref{fig:recruits}.

### Reference Points

Reference points were calculated using the estimated selectivity and catch distributions among fleets in the most recent year of the model (`r endyr`, Table \ref{tab:referenceES}). Sustainable total yields  were `r round(model$derived_quants[model$derived_quants$Label == 'Dead_Catch_SPR', 'Value'], 2)` mt when using an $SPR_{50\%}$ reference harvest rate. The spawning output equivalent to 40 percent of the unfished spawning output ($SB_{40\%}$) was `r round(model$derived_quants[model$derived_quants$Label == 'SSB_SPR', 'Value'], 2)` millions of eggs. 

The `r endyr` spawning output relative to unfished equilibrium spawning output is above the target of 40 percent of unfished spawning output (Figure \ref{fig:depl}). The fishing intensity, $1-SPR$, has been above the harvest rate limit ($SPR_{50\%}$) in nearly all years from 1977-2001, and in all but 2015 and 2016 since 2011 (Table \ref{tab:timeseries} and Figure \ref{fig:1-spr}). Table \ref{tab:referenceES} shows the full suite of estimated reference points for the base model and Figure \ref{fig:yield} shows the equilibrium curve based on a steepness value fixed at `r model$parameters[model$parameters$Label == "SR_BH_steep","Value"]`.

<!--chapter:end:33results.Rmd-->

## Model Diagnostics

### Convergence

Proper convergence was determined by starting the minimization process from dispersed values of the maximum likelihood estimates and adjusting phases of the estimated parameters to determine if the model found a better minimum. Starting parameters were jittered by 10 percent. This was repeated 100 times with 33 out of 100 runs returned to the base model likelihood. A better, lower negative log-likelihood, model fit was not found. Early exploration runs did reveal some convergence issues that were identified through jittering, and were resolved by updating data weighting values suggested from a run starting with the the initial values set at parameter estimates. Through the jittering done as explained, likelihood profiles, and alternative phasing, we are confident that the base model as presented represents the best fit to the data given the assumptions made. There were no difficulties in inverting the Hessian to obtain estimates of variability throughout initial model attempts and all explorations resulted in a positive-definite Hessian. 

[need to do alternative phasing]

### Likelihood Profiles

Likelihood profiles were conducted for $R_0$, steepness, natural mortality, $L_{\infty}$, and growth coefficient ($k$) values separately. These likelihood profiles were conducted by fixing the parameter at specific values and estimating the remaining parameters based on the fixed parameter value. 

In regards to values of $R_0$, the negative log-likelihood was minimized at approximately a log($R_0$) of `r round(log(model$derived_quants[model$derived_quants$Label == "Recr_Virgin",2]),2)` (Figure \ref{fig:r0-profile}). The recreational data supported lower log($R_0$) values whereas the commercial data supported higher log($R_0$) values. Increasing the $R_0$, relative to the value estimated, results in an a sharp increase in stock scale (Figure \ref{fig:r0-ssb}) and status  and (Figure \ref{fig:r0-depl}). Estimates of derived quantities across the range of profiled values of log($R_0$) are shown in Table \ref{tab:profile_r0}.

For steepness, values from approximately 0.6 to 0.8 were supported with the lowest negative log-likelihood occurring at the upper bound of 1.0 (Figure \ref{fig:h-profile}). Assuming higher or lower steepness values had little impact on the recent unfished and spawning output estimated for all but the lowest values (Figure \ref{fig:h-ssb}). The estimated relative final stock status was above 0.40 of unfished biomass across steepness values except for the lowest values (0.30 and 0.40) (Figure \ref{fig:h-depl}). Estimates of derived quantities across the range of profiled values of steepness are shown in Table \ref{tab:profile_h}.

The negative log-likelihood profile across natural mortality supported values between 0.045 and 0.09 (the highest value in the profile) which included the fixed value of `r model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"]` (Figure \ref{fig:m-profile}). The estimated stock trajectories assuming lower or higher natural mortality values impacted the estimated unfished spawning output (Figures \ref{fig:m-ssb}) and resulted in a wide range of stock statuses (Figures \ref{fig:m-depl}) from below, within, and above the management precautionary zone (between 0.25 - 0.40). Estimates of derived quantities across the range of profiled values of $M$ are shown in Table \ref{tab:profile_m}.

A profile across a range of $L_{\infty}$ values was also conducted (Figure \ref{fig:linf-profile}). The negative log-likelihood was minimized near the fixed value of `r model$parameters[model$parameters$Label == "L_at_Amax_Fem_GP_1","Value"]`. The recreational data supported slightly higher $L_{\infty}$ values whereas the commercial data supported lower $L_{\infty}$ values. The stock scale and status is quite variable across alternative $L_{\infty}$ values where assuming lower values resulted in sharp increases in stock scale (Figure \ref{fig:linf-ssb}) and status (Figure \ref{fig:linf-depl}). Estimates of derived quantities across the range of profiled values of $L_{\infty}$ are shown in Table \ref{tab:profile_linf}.

A profile across a range of $k$ values was also conducted (Figure \ref{fig:k-profile}). The negative log-likelihood showed support for values between 0.135 and 0.21, and was minimized at 0.165 with support from both the recreational and commercial data. The $k$ value for fish in the model was fixed at `r model$parameters[model$parameters$Label == "VonBert_K_Fem_GP_1","Value"]`. The stock scale (Figure \ref{fig:k-ssb}) and status (Figure \ref{fig:k-depl}) increased under lower $k$ values. Estimates of derived quantities across the range of profiled values of $k$ are shown in Table \ref{tab:profile_k}.

### Retrospective Analysis

A five-year retrospective analysis was conducted by running the model using data up to 2015, 2016, 2017, 2018, and 2019. The estimated spawning output (Figures \ref{fig:retro-ssb}) and stock status (Figure \ref{fig:retro-depl}) declined in comparison with the base model as recent years of data were removed. Removing the first 1-4 years of data resulted in a steady decline is spawning output relative to the base model likely due to reducing the information about the recruitment pulse in 2012 from the lengths comps. The effect of removing the fifth year was inconsistent with other years likely given the limited information in 2016 when retention was prohibited in the Oregon recreational fishery. 

### Sensitivity Analyses

A number of sensitivity analyses were conducted. Sensitivities were conducted as a single exploration from the base model assumptions and/or data, and were not performed in a cumulative fashion.

\begin{enumerate}
   
  \item Deterministic recruitment from the stock recruitment curve. 

  \item Data weighting according to the McAllister-Ianelli method (MI DW) using the weighting values shown in Table \ref{tab:dw}. 
  
  \item Data weighting according to the Dirichlet Multinomial method (DM DW) where the estimated parameters are shown in Table \ref{tab:dw}. 

  \item Estimate $L_{\infty}$.
  
  \item Estimate $L_{\infty}$ and $k$.

  \item Estimate the coefficient of variation in length of older fishes.

  \item Estimate natural mortality.
  
  \item Exclude composition data prior to 2001 for recreational fleets

  \item Fix recreational selectivity form to be asymptotic. 
  
  \item Allow commercial selectivity form to be dome-shaped.

  \item Estimate recreational selectivity block: 1979-1999 with asymptotic selectivity curve and 2000-2020 with dome-shaped selectivity.   
  
\end{enumerate}

Likelihood values and estimates of key parameters from each sensitivity are available in Table \ref{tab:sensitivities}. Plots of the estimated time-series of spawning biomass and relative spawning biomass are shown in Figures \ref{fig:sens-ssb} and \ref{fig:sens-depl}, respectively.

The largest change from the base model resulted when recruitment was fixed to be deterministic, and when selectivity for the recreational fleet was set to be asymptotic. Assuming deterministic recruitment resulted in a higher stock scale, and different biomass trajectory, but a comparable stock status relative to the base model. Assuming asymptotic selectivity for the recreational fleet resulted in a reduction in the scale and status of the stock, such that biomass in 2020 relative to unfished biomass was close to the threshold of 25 percent. 

Four additional sensitivities either had changes in stock scale of greater than 10 percent from the base model or had stock status between the management precautionary zone (between the target and threshold ratio values). Estimating $L_{\infty}$ and $L_{\infty}$ and $k$ resulted in similarly low stock scale compared to the sensitivity with asymptotic selectivity for the recreational fleet. Estimating $L_{\infty}$ resulted in a more pessimistic view of stock status compared to the base, with biomass in 2020 relative to unfished biomass estimated between the threshold and target ratios. Data weighting with the McAllister-Ianelli (MI) approach also resulted in biomass in 2020 relative to unfished biomass being between the threshold and target ratios, however the scale was similar to the base model. Estimating variation in length for older fish resulted in an increased stock scale, but similar stock status as the base model. 

Data weighting with the Dirichlet-Multinomial, estimating natural mortality, excluding early recreational length comps or fitting them with a different selectivity curve, and allowing dome-shaped selectivity for the commercial fleet produced similar results as the base model.


### Unresolved Problems and Major Uncertainties

There were four primary uncertainties in the model given current data availability and model assumptions. 
\begin{enumerate}

  \item First, selectivity form for the recreational fleet was a major source of uncertainty, not only affecting the scale of the population but also resulting in relative stock size near the lower edge of the management precautionary zone. 
  
  \item Second, the magnitude of recruitment deviations was a source of uncertainty. Strong recruitment pulses in 1993, 1995, 1999, and 2012 were often estimated during model exploration with some years being stronger in some runs compared to others. Recruitment deviations in other years during the 1990s were typically variable, and sometimes greatly so as shown in (Figure \ref{fig:rec-devs}). These were likely due to limited samples and variable length in the recreational length compositions. This variation influences the magnitude of the increase in biomass in the late 1990s and  2000s as well as the magnitude of the decrease in the 2010s. Omitting recruitment deviations altogether changes the scale of the model as well. 
  
  \item The magnitude of recruitment was also affected by the data weighting values, which is the third uncertainty. Data weighting using McAllister-Ianelli reduced the amount of information coming from the recreational fleet, affecting the magnitude of recruitment, and resulting in a more pessimistic stock status. Francis and the Dirichlet-Multimonial weighting resulted in similar results. 
  
  \item The final uncertainty is estimates of growth. The fixed value for k for `r spp` is on the higher end of other published studies, ranging between 0.06-0.19, and results in a low $M$/$k$ ratio. Profiles and sensitivities for $L_{\infty}$ and $k$ suggest estimating these parameters is feasible, both separately and together, and result in estimates of $k$ nearer to the middle of the range of literature values and $L_{\infty}$ close to the fixed estimate. We decided to keep the fixed values in the base model given the range of plausible $k$ values from the profile included the fixed estimate, and that growth estimates included a fairly large number of young fish from the surveys to inform the esitmate of $k$.  
  
\end{enumerate}


<!--chapter:end:34diagnostics.Rmd-->

# Management 

## Harvest Projections and Decision Tables

A ten year projection of the base model with catches equal to the estimated Acceptable Biological Catch (ABC) based on the category 2 time-varying sigma and $P^*$ = 0.45 for years 2023-2032 (Table \ref{tab:project}). The removals in 2021 and 2022 were set based on the adopted Annual Catch Limits (ACLs) and the percent allocation (58.4 percent) for `r state` provided by the PFMC Groundfish Management Team (GMT, personal communication). ACLs were apportioned to recreational and commercial catches based on the average proportion from 2018-2020 each fleet contributes to the total catch. 

The decision table uncertainty axes and catch levels are to be determined later.

<!-- Evaluation of Scientific Uncertainty -->

```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'4_management_uncertainty.Rmd')
read_child(filein)
```

# Research and Data Needs

The ability to estimate additional process and biological parameters for `r spp` was limited by data.  Collecting the following data would be beneficial to future assessments of the stock:

\begin{itemize}

	\item Continue collecting length and otolith samples from recreational and commercial catches, as well as from surveys, which capture small `r spp`.

	\item Improved understanding of where recreational fishing is commonly occuring (areas and depths) and the range of sizes available by depth would be beneficial to better inform the selectivity form.  
	
	\item Recruitment patterns showed lower than average recruitment in the 2000s. Additional data to support such patterns in recruitment would provide additional support for model estimates.  
	
\end{itemize}


## Comparisons with state-based fishery-independent surveys 

Fishery-independent surveys along the Oregon coast have been conducted by the ODFW. 

[maybe put in a different section?]
[more info on Oregon surveys, need to update reference earlier]

<!--chapter:end:40management.Rmd-->

<!-- Acknowledgments -->
```{r, echo=FALSE, results='asis'}
filein = file.path(general_wd,'41_acknowledgments.Rmd')
read_child(filein)
```

<!--chapter:end:41acknowledgments.Rmd-->

\clearpage

# References
<!-- If you want to references to appear somewhere before the end, add: -->
<div id="refs"></div>
<!-- where you want it to appear -->
<!-- The following sets the appropriate indentation for the references
  but it cannot be used with bookdown and the make file because it leads
  to a bad pdf.
\noindent
\vspace{-2em}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
 -->

<!--chapter:end:49bibliography.Rmd-->

\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

<!-- tab:catch -->
\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/Catches_All_Years.tex}

\newpage


```{r, results = 'asis'}
yrs = hist = 2011:2020
nfleets = 2
catch = dead = total.dead = 0
for (i in 1:nfleets){
  name = paste0("retain(B):_",i)
  input.catch = model$timeseries[model$timeseries$Yr %in% yrs, name]
  catch = cbind(catch, input.catch)
}
total.catch <- round(apply(catch, 1, sum),2)

man = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")
man = man[man$Year %in% yrs, ]
out = cbind(round(man,2), round(man$ACL * 0.584, 2), total.catch)

col_names = c("Year", "OFL", "ACL", "OR ACL", "OR Removals")

table_format(x = out,
             caption = "The OFL and ACL for the Minor Nearshore Rockfish North complex, the ACL allocated to Oregon, and the total removals.",
             label = "ofl",
             align = 'l',
             col_names = col_names)


```

\newpage


<!-- ======================================================= -->
<!-- ***************       Data      *********************** --> 
<!-- ======================================================= -->


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/OR_Samples_Feb2021.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/or_rec_samples.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/len_at_age_data.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/len_at_weight_data.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/or_rec_age_samples.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/OR_age_Samples_Feb2021.tex}

\newpage

<!-- ======================================================= -->
<!-- ***************    Biology      *********************** --> 
<!-- ======================================================= -->

```{r, results='asis'}

growth = model$endgrowth[model$endgrowth$Sex == 1, ]
out = growth[, c("Age_Beg", "Len_Beg", "Wt_Beg", "Len_Mat", "Mat*Fecund")]
out$Len_Mat[out$Len_Mat > 0.99] = 1
rownames(out) = NULL
col_names = c('Age', 'Length (cm)', 'Weight (kg)', 'Maturity', 'Spawning Output')

table_format(x = out[1:51,],
             caption = "Age, length, weight, maturity, and spawning output by age (product of maturity and fecundity) at the start of the year. Output for ages 51-95 is truncated as these ages have the same length, weight, maturity, and spawning output as at age 50.",
             label = "growth-tab",
             digits = c(0, 2, 2, 2, 2),
             align = 'l',
             col_names = col_names,
             longtable = TRUE) 

```

\newpage

<!-- ======================================================= -->
<!-- ***************  Data Weights   *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'data_weights.csv'))

col_names = c('Method',
        'Commercial Lengths',
              'Recreational Lengths')
table_format(x = tab,
             caption = "Data weights applied by each alternative data weighting methods. The Dirichlet Multinomial weight is theta/(1+theta)",
             label = "dw",
             align = 'l',
             col_names = col_names)
```

<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}

mod_params = model$parameters[-c(grep('Impl',model$parameters$Label),
							     grep('Fore',model$parameters$Label)),
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 

test = mod_params[which(mod_params$Label == "Wtlen_1_Fem_GP_1"),'Value']
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 

# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')

# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))

# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Fem_GP_1",3]), 3)

# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])

#Reformat so can show a value for alpha in length-weight relationship
mod_params[,"Value"] = format(mod_params$Value, digits = 2)
mod_params[which(mod_params$Label == "Wtlen 1 Fem GP 1"), "Value"] = test

# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')

table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("6cm", "4cm"))                         

```
<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

<!-- tab:likes -->
\include{tex_tables/likelihoods.tex}


<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

<!-- tab:timeseries -->
\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/TimeSeries.tex}

\newpage

<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->

<!-- tab:sensitivities -->
\include{tex_tables/sensitivities.tex}

\newpage

<!-- ======================================================= -->
<!-- ****************         SSS            *************** --> 
<!-- ======================================================= -->

<!-- \input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/sss_40.tex} -->

<!-- \newpage -->

<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/e_ReferencePoints_ES.tex}

\newpage


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'g_Projections_ES.csv'))
man = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")

out = cbind(tab$Year,
            c(man[man$Year %in% c(2021, 2022), "OFL"], rep("-",10)),
            c(man[man$Year %in% c(2021, 2022), "ACL"], rep("-",10)),
            c(round(man[man$Year %in% c(2021, 2022), "ACL"] * 0.584,2), rep("-", 10)),
            c(rep("-",2), round(tab[3:12,2], 2)),
            c(rep("-",2), round(tab[3:12,3],2)),
            c(rep("-",2), round(tab[3:12,3]/tab[3:12,2], 3)),
            round(tab[ ,5:ncol(tab)], 2))

col_names = c('Year',
              'Adopted OFL',
              'Adopted ACL',
              "Adopted ACL-OR",
              "OFL", 
              "ABC", 
              "Buffer",
              "Spawning Output",
              "Fraction Unfished")
table_format(x = out,
             caption = "Projections of potential OFLs (mt), ABCs (mt), estimated spawning output, and fraction unfished. The OFL, ACL, and Oregon (OR) ACL for 2021 and 2022 reflect adopted management limits.",
             label = "project",
             align = 'l',
             col_names = col_names)
```

\newpage

<!-- ======================================================= -->
<!-- ********  Profiles *************** -->
<!-- ======================================================= -->

```{r, results = 'asis'}
#R0 profile
tab = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/or", "7_1_0_baseProfile_profile_SR_LN(R0)", 'profile_SR_LN(R0)_results.csv'))
#col_names = paste0("R0_",round(tab$parameter_value,2))
#profile_table = data.frame(t(tab[,4:9]))
profile_table = tab[3:9]
colnames(profile_table)[1] = "parameter value"
col_names = c(colnames(profile_table))

table_format(x = profile_table,
             caption = "Derived quantities for the profile of values of the logarithm of equilbirum recruitment.",
             label = "profile-r0",
             align = 'l',
             font_size = 9,
             digits = 3,
             col_names = col_names)
```

\newpage

```{r, results = 'asis'}
#Steepness profile
tab = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/or", "7_1_0_baseProfile_profile_SR_BH_steep", 'profile_SR_BH_steep_results.csv'))
#profile_names = paste0("h_",round(tab$parameter_value,2))
#profile_table = data.frame(t(tab[,4:9]))
profile_table = tab[3:9]
colnames(profile_table)[1] = "parameter value"
col_names = c(colnames(profile_table))

table_format(x = profile_table,
                 caption = 'Derived quantities for the profile of values of steepness',
                 label = 'profile-h',
                 font_size = 9,
                 digits = 3,
                 col_names = profile_names)
```
\newpage

```{r, results = 'asis'}
#M profile
tab = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/or", "7_1_0_baseProfile_profile_NatM_p_1_Fem_GP_1", 'profile_NatM_p_1_Fem_GP_1_results.csv'))
#profile_names = paste0("M_",round(tab$parameter_value,2))
#profile_table = data.frame(t(tab[,4:9]))
profile_table = tab[3:9]
colnames(profile_table)[1] = "parameter value"
col_names = c(colnames(profile_table))

table_format(x = profile_table,
                 caption = 'Derived quantities for the profile of values of natural mortality',
                 label = 'profile-m',
                 font_size = 9,
                 digits = 3,
                 col_names = profile_names)
```
\newpage

```{r, results = 'asis'}
#Linf profile
tab = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/or", "7_1_0_baseProfile_profile_L_at_Amax_Fem_GP_1", 'profile_L_at_Amax_Fem_GP_1_results.csv'))
#profile_names = paste0("L_at_Amax_",round(tab$parameter_value,2))
#profile_table = data.frame(t(tab[,4:9]))
profile_table = tab[3:9]
colnames(profile_table)[1] = "parameter value"
col_names = c(colnames(profile_table))

table_format(x = profile_table,
                 caption = 'Derived quantities for the profile of values of length at maximum age',
                 label = 'profile-linf',
                 font_size = 9,
                 digits = 3,
                 col_names = profile_names)
```
\newpage

```{r, results = 'asis'}
#K profile
tab = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/or", "7_1_0_baseProfile_profile_VonBert_K_Fem_GP_1", 'profile_VonBert_K_Fem_GP_1_results.csv'))
#profile_names = paste0("R0_",round(tab$parameter_value,2))
#profile_table = data.frame(t(tab[,4:9]))
profile_table = tab[3:9]
colnames(profile_table)[1] = "parameter value"
col_names = c(colnames(profile_table))

t = table_format(x = profile_table,
                 caption = 'Derived quantities for the profile of values of von Bertalannfy growth coefficient',
                 label = 'profile-k',
                 font_size = 9,
                 digits = 3,
                 col_names = profile_names)
```
\newpage

<!--chapter:end:52tables.Rmd-->

\clearpage
# Figures


<!-- ====================================================================== -->  
<!-- ****************** Catches Used in the Model ************************* --> 
<!-- ====================================================================== -->  

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "catch2 landings stacked.png"), 
caption = "Catches by fleet used in the base model",
label = 'catch')
```	


<!-- ====================================================================== --> 
<!-- ******************* Data Used in the Model *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "data_plot.png"), 
caption = "Summary of data sources used in the base model",
label = 'data-plot')
```	


<!-- ====================================================================== -->
<!-- ****************   Commercial Length Samples    ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_bubflt1mkt0_page2.png"), 
caption = "Length composition data from the commercial fleet",
label = 'com-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_data_weighting_TA1.8_OR_Commercial.png"), 
caption = "Mean length for commercial fleet with 95 percent confidence intervals",
label = 'mean-com-len-data')
```


<!-- ====================================================================== -->
<!-- **************** Recreational Length Samples    ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_bubflt2mkt0_page3.png"), 
caption = "Length composition data from the recreational fleet",
label = 'rec-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_data_weighting_TA1.8_OR_Recreational.png"), 
caption = "Mean length for recreational fleet with 95 percent confidence intervals",
label = 'mean-rec-len-data')
```

<!-- ====================================================================== -->
<!-- *************************     Biology     **************************** --> 
<!-- ====================================================================== -->


<!-- =================== -->
<!-- ==  Possibly revise  == -->
```{r, results = 'asis'}
add_figure(
filein = file.path(data_fig_loc, "Length_Weight_by_Source.png"), 
caption = "Comparison of the length-at-weight data from the individual sources with length and weight data, and with all sources combined.",
label = 'len-weight-survey')
```	

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio5_weightatsize.png"), 
caption = "Weight-at-length by sex used in the model",
label = 'len-weight')
```	

<!-- =================== -->
<!-- ==  Possibly revise  == -->
```{r, results = 'asis'}
add_figure(
filein = file.path(data_fig_loc, "Length_Age_by_Sex.png"), 
caption = "Observed sex specific length-at-age coastwide data by data source with the estimated length-at-age curve",
label = 'len-age-data')
```	


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio1_sizeatage.png"), 
caption = "Length at age in the beginning of the year in the ending year of the model",
label = 'len-age-ss')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio6_maturity.png"), 
caption = "Maturity as a function of  length",
label = 'maturity')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio9_fecundity_len.png"), 
caption = "Fecundity as a function of length",
label = 'fecundity')
```

<!-- =================== -->
<!-- ==  Need to do the following two  == -->

<!-- ```{r, results = 'asis'} -->
<!-- add_figure( -->
<!-- filein = file.path(data_fig_loc, "Length_fraction_female.png"),  -->
<!-- caption = "Fraction female by length across all available data sources", -->
<!-- label = 'len-sex-ratio') -->
<!-- ``` -->

<!-- ```{r, results = 'asis'} -->
<!-- add_figure( -->
<!-- filein = file.path(data_fig_loc, "Age_fraction_female.png"),  -->
<!-- caption = "Fraction female by age across all available data sources", -->
<!-- label = 'age-sex-ratio') -->
<!-- ``` -->


<!-- ====================================================================== -->
<!-- *********************    Selectivity            ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "sel01_multiple_fleets_length1.png"),
caption = "Selectivity at length by fleet",
label = 'selex')
```

<!-- ====================================================================== -->
<!-- *********************    Recruitment            ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts11_Age-0_recruits_(1000s)_with_95_asymptotic_intervals.png"), 
caption = "Estimated time series of age-0 recruits (1000s)",
label = 'recruits')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "recdevs2_withbars.png"), 
caption = "Estimated time series of recruitment deviations",
label = 'rec-devs')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "recruit_fit_bias_adjust.png"),
caption = "Recruitment bias adjustment applied in the base model",
label = 'bias-adj')
```


<!-- ====================================================================== -->
<!-- ****************** Fit to the Length Data **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_residsflt1mkt0_page2.png"), 
caption = "Pearson residuals for commercial fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-pearson')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_data_weighting_TA1.8_OR_Commercial.png"), 
caption = "Model estimated mean length (blue line) overlaid on mean length of commercial lengths (gray circles) with 95 percent confidence intervals based on current samples sizes",
label = 'com-mean-len-fit')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_residsflt2mkt0_page3.png"), 
caption = "Pearson residuals for recreational fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-pearson')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_data_weighting_TA1.8_OR_Recreational.png"), 
caption = "Model estimated mean length (blue line) overlaid on mean length for recreational lengths (gray circles) with 95 percent confidence intervals based on current samples sizes",
label = 'rec-mean-len-fit')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit__aggregated_across_time.png"), 
caption = "Aggregated length comps over all years",
label = 'agg-len-fit')
```

<!-- ====================================================================== -->
<!-- ******************      Time Series       **************************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning output",
label = 'ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts1_Total_biomass_(mt).png"), 
caption = "Estimated time series of total biomass",
label = 'tot-bio')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of relative spawning output",
label = 'depl')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "UnavailableSpawningOutput.png"),
caption = "Proportion of biomass unavailable due to selectivity for small and large fish.",
label = 'unavail-bio')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "SR_curve.png"), 
caption = "Stock-recruit curve. Point colors indicate year, with warmer colors indicating earlier years and cooler colors in showing later years",
label = 'bh-curve')
```



<!-- ====================================================================== -->
<!-- ******************    Reference Points    **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "SPR2_minusSPRseries.png"), 
caption = "Estimated 1 - relative spawning ratio (SPR) by year",
label = '1-spr')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model. Values are based on the 2020
fishery selectivity and with steepness fixed at 0.72",
label = 'yield')
```


<!-- ====================================================================== -->
<!-- ******************       Sensitivity     ***************************** --> 
<!-- ====================================================================== -->

```{r, echo=FALSE, results='asis'}
sens_wd = file.path("C:/Users/Brian.Langseth/Desktop/or", "sensitivities")
nm = "base.710_sensitivities_compare2_spawnbio_uncertainty.png"
add_figure(
filein = file.path(sens_wd, nm),
caption = "Change in estimated spawning output by sensitivity",
label = 'sens-ssb')
```

```{r, echo=FALSE, results='asis'}
nm = "base.710_sensitivities_compare4_Bratio_uncertainty.png"
add_figure(
filein = file.path(sens_wd, nm),
caption = "Change in estimated fraction unfished by sensitivity",
label = 'sens-depl')
```

<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- nm = "base.710_sensitivities_compare12_recdevs_uncertainty.png") -->
<!-- add_figure( -->
<!-- filein = file.path(sens_wd, nm), -->
<!-- caption = "Change in estimated annual recruitment deviation", -->
<!-- label = 'sens-recdev') -->
<!-- ``` -->

<!-- ====================================================================== -->
<!-- ******************      Likelihoods      ***************************** --> 
<!-- ====================================================================== -->

<!-- R0 -->
```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_LN(R0)"),  "piner_panel_SR_LN(R0).png"), 
caption = "Change in the negative log-likelihood across a range of log(R0) values",
label = 'r0-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_LN(R0)"),  "SR_LN(R0)_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of log(R0) values",
label = 'r0-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_LN(R0)"),  "SR_LN(R0)_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of log(R0) values",
label = 'r0-depl')
```

<!-- h -->
```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_BH_steep"),  "piner_panel_SR_BH_steep.png"), 
caption = "Change in the negative log-likelihood across a range of steepness values",
label = 'h-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_BH_steep"),  "SR_BH_steep_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of steepness values",
label = 'h-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_BH_steep"),  "SR_BH_steep_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of steepness values",
label = 'h-depl')
```

<!-- M -->
```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_NatM_p_1_Fem_GP_1"),  "piner_panel_NatM_p_1_Fem_GP_1.png"), 
caption = "Change in the negative log-likelihood across a range of female natural mortality values",
label = 'm-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_NatM_p_1_Fem_GP_1"),  "NatM_p_1_Fem_GP_1_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of female natural mortality values",
label = 'm-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_NatM_p_1_Fem_GP_1"),  "NatM_p_1_Fem_GP_1_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of female natural values",
label = 'm-depl')
```

<!-- Linf -->
```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_L_at_Amax_Fem_GP_1"),  "piner_panel_L_at_Amax_Fem_GP_1.png"), 
caption = "Change in the negative log-likelihood across a range of female maximum length values",
label = 'linf-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_L_at_Amax_Fem_GP_1"),  "L_at_Amax_Fem_GP_1_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of female maximum length values",
label = 'linf-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_L_at_Amax_Fem_GP_1"),  "L_at_Amax_Fem_GP_1_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of female maximum length values",
label = 'linf-depl')
```

<!-- k -->
```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_VonBert_K_Fem_GP_1"),  "piner_panel_VonBert_K_Fem_GP_1.png"), 
caption = "Change in the negative log-likelihood across a range of female k values",
label = 'k-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_VonBert_K_Fem_GP_1"),  "VonBert_K_Fem_GP_1_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of female k values",
label = 'k-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_VonBert_K_Fem_GP_1"),  "VonBert_K_Fem_GP_1_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of female k values",
label = 'k-depl')
```


<!-- ====================================================================== -->
<!-- ******************     Retrospectives    ***************************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_retro"),  "compare2_spawnbio_uncertainty.png"), 
caption = "Change in the estimate of spawning output when the most recent 5 years of data area removed sequentially",
label = 'retro-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_retro"),  "compare4_Bratio_uncertainty.png"),
caption = "Change in the estimate of fraction unfished when the most recent 5 years of data area removed sequentially",
label = 'retro-depl')
```


\newpage

<!--chapter:end:53figures.Rmd-->

\clearpage

# Appendix 

## Detailed Fit to Length Composition Data 


```{r, results='asis'}
plot_info = read.csv(file.path(mod_loc, "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = c(grep("comp_lenfit_flt", len_fit$label),grep("comp_gstlenfit_flt", len_fit$label))
filein = file.path(mod_loc, "plots")

for (a in plot.vec){
	cap = len_fit$caption[a]
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab)
}
```

\clearpage


## ODFW Marine Reserve Hook and Line Survey

One source of information that fell outside the bounds of the current PFMC Groundfish Terms of Reference for Data Moderate assessment is the ODFW Marine Reserve Hook and Line Survey. This data source to date has not been used in any West Coast groundfish stock assessments, but will likely be considered in select future full rockfish assessments (e.g., black rockfish). Given that this is an existing data source that may prove useful for future rockfish assessments, we wanted to provide an overall summary of this data source and the available data for `r spp`.

The Marine Reserve Program in the ODFW has routinely monitored state marine reserves (MR) and associated comparison areas (CA) since 2011. Data from the hook and line survey from 2011 - 2019 are presented in this summary. Surveys in 2011 and 2012 only visited a single site, Redfish Rocks. Surveys from 2013 – 2019 include reserves and comparison areas from four sites: Redfish Rocks, Cape Falcon, Cape Perpetua and Cascade Head. Each of these four sites has a marine reserve and one to three comparison areas. Comparison areas are specifically selected for each marine reserve to be similar in location, habitat and depth to the reserve but are subject to fishing pressure. Not all sites are sampled in each year, due to both the gradual implementation of the reserve network and the available staff to execute surveys. Sites and areas sampled that are included in this dataset are below.  


```{r, results = 'asis'}
data = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys/table_1_sample_info.csv")

col_names = c("Site", "Area", "Years Sampled", "Total Samples")
table_format(x = data,
             caption = "Sites and areas sampled by the Marine Reserve Program hook and line survey.",
             label = "table-1",
             align = 'l',
             custom_width = TRUE,
             col_to_adjust = 1:4,
             width = c('2.2cm', '5.75cm', '3.5cm', '1.25cm'),
             col_names = col_names)
```

A 500 meter square grid overlaid on the sampling area defines the sample units or cells. Cells are randomly selected within a marine reserve or comparison area for each sampling event. Three replicate drifts are executed in each cell. The specific location of the drifts within the cell is selected by the captain. Over time, cells without appropriate habitat for the focus species, mainly groundfish, have been removed from the selection procedures, and those presented in this dataset include only those that are currently "active". The number of cells visited in a day can vary slightly and range from three to five. Data are aggregated to the cell-day level.

### Quillback Rockfish Summary   

Of the 940 total-cell days at 14 areas, 164 (17.4 percent) of those had positive `r spp` catches with a total of 291 observations of `r spp` across all years and sites. The number of `r spp` caught ranged from 1 to 10 fish in a cell-day. 

```{r, results = 'asis'}
data = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys/table_2_marine_hkl.csv")

col_names = c("", "2011", "2012", "2013", "2014", "2015", "2016", "2017", "2018", "2019", "Total")
table_format(x = data,
             caption = "Summary of number of catch cell days and positive observations of quillback rockfish.",
             label = "table-2",
             align = 'l',
             landscape = TRUE,
             col_names = col_names)
```

```{r, results = 'asis'}
loc = "//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys"
add_figure(
filein = file.path(loc,  "fig_1_marine_hkl.png"), 
caption = "Frequency of positive quillback rockfish catches between 2011 - 2019",
label = 'pos-hkl')
```

Areas  differ in both geographic location and the level of fishing pressure experienced or allowed. Staff from the Marine Reserves Program suggested that the treatment (reserve vs. comparison area) may not be a delineating factor for the catch of some species (e.g., cabezon) due to the recent implementation of the reserves. It was suggested that data could be aggregated to the site level, functioning at the level of a reef complex, to examine patterns at different locations along the coast. However, this may not be possible with the sample size available at some sites.

Observations of `r spp` were varied across sample sites and years. The number of observations of `r spp` was highest at Redfish Rocks (N = 118) and closely followed by Cape Perpetua (N = 108).  

```{r, results = 'asis'}
data = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys/table_3_data.csv")

data = data[-nrow(data),]

col_names = c("Site", "Year", "Number of Positive Catch Cell Days", "Total Cell Days", "Proportion of Positives", "Total Number of Quillback Rockfish Caught")
table_format(x = data,
             caption = "Summary of sampling effort by year and site combined with the positive observations of quillback rockfish.",
             label = "table-3",
             align = 'l',
             digits = c(0, 0, 0, 0, 3, 0), 
             col_names = col_names)
```


Catch-per-unit-effort (CPUE) was calculated by the number of fish per angler hour. The number of anglers and hooks are standardized for each survey. Angler hours have been adjusted for non-fishing time (i.e., travel time, etc.).

```{r, results = 'asis'}
loc = "//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys"
add_figure(
filein = file.path(loc,  "fig_2_cpue_val.png"), 
caption = "Quillback rockfish CPUE calculated based on positive values only",
label = 'fig-2')
```

```{r, results = 'asis'}
loc = "//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys"
add_figure(
filein = file.path(loc,  "fig_3_cpue.png"), 
caption = "Quillback rockfish CPUE calculated based on all values",
label = 'fig-3')
```

Additional filtering may not be necessary, as the filtering for "active" cells has already likely removed any unsuitable sampling units, based on habitat, depth and local knowledge.  Based on the annual proportion of positive cell-days and the relative rarity of `r spp` encounters, there are probably not enough data to move forward with a timeseries at a coastwide level. However, Redfish Rocks has been sampled in each year from 2011 - 2019, except for 2018. Though sample size is extremely limited, CPUE based on positive values at this site shows a variable and slightly declining trend from 2011 to 2015 followed by a slightly increasing trend from 2015 to 2020 for `r spp`. This differs from the trajectory from the base model in which shows a decline from 2016 to 2020 (Figure \ref{fig:tot-bio}).

```{r, results = 'asis'}
loc = "//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys"
add_figure(
filein = file.path(loc,  "fig_4_redfish_cpue.png"), 
caption = "Quillback rockfish CPUE calculated at Redfish Rocks based on postive values only",
label = 'fig-4')
```

When all sties and all values are included, `r Spp` appear to have a relatively stable trend from 2011 – 2019, with the annual mean CPUE oscillating around the long-term mean. 


```{r, results = 'asis'}
loc = "//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/OR state surveys"
add_figure(
filein = file.path(loc,  "fig_5_relative_cpue.png"), 
caption = "Quillback rockfish relative CPUE across all sample sites and with all data values",
label = 'fig-5')
```

### Video Lander Population Estimate

Oregon Department of Fish and Wildlife (ODFW) provided density estimates and a range of estimated population abundances from underwater video lander data for quillback rockfish (Sebastes maliger). The lander data was collected over nine years by the ODFW and summarized in Rasmuson et al. ([@rasmuson_lander_2020]). This large dataset is made up of ten independent studies carried out in both nearshore rocky reefs coastwide as well as select reef structures offshore of the central coast of Oregon. Underwater video landers are stationary platforms consisting of one to three video cameras. Landers used in deeper water employ advanced lighting systems for optimal viewing of fish and benthic habitat. Ambient light is used in shallow surveys. The variability in detection range by depth is an important factor to consider when deriving fish density from lander data. Therefore, a series of abundance estimates were provided to inform the quillback rockfish assessment.  Methods are summarized below but a more detailed document is available by ODFW upon request.  

Variability in range (and therefore, area viewed) directly influences fish abundance; therefore, fish density estimates were calculated using five different estimates of range. These include the average range, the range +/- one standard deviation from the mean, and the maximum and minimum ranges. The area viewed is calculated using both the range and the horizontal field of view. This viewed area was then combined with fish count data to generate fish densities. Count data were provided from Rasmuson et al. (2020). As expected, the viewed range has a large effect on the calculated density of the fish, with larger ranges resulting in a lower density of fish. Since there is no way to know which range model most accurately reflects the true density of fish, multiple range estimates were combined into a single density estimate using a weighted arithmetic mean. Although the arithmetic mean is simpler and more intuitive, the fact that the area viewed increases exponentially suggests a geometric mean may be more appropriate. As an alternative to the arithmetic mean, the geometric mean density was calculated in three different ways to address the zeros in the data. Abundance estimates (numbers of fish) were calculated by multiplying the density estimate by an estimate of the habitat area. Coastwide habitat area was limited to primary or secondary habitat containing hard substrate. The western boundary was defined as the 200 m contour based on the depth of the continental shelf-break. The eastern boundary was based on the shallowest lander observation for each species. Quillback rockfish were not observed on lander video in water <22 m, therefore the 20 m contour was used. It should be noted that while the depth range of the lander surveys conducted by ODFW extends to 212 m, the majority of lander surveys have been conducted in either nearshore rocky reefs or at Stonewall Bank RCA on the central Oregon coast. 

Abundance estimates for the coastwide survey area are provided for quillback rockfish derived from each of the nine density estimates; five range models, the weighted arithmetic mean, and three weighted geometric mean methods. For quillback rockfish, density estimates ranged from 0.004 ± 0.029 (no. fish / m2 ± SD) from the maximum range method to 0.950 ± 1.366 for the third geometric mean method. The estimated habitat area was 1,840 thousands of km2. Abundance estimates ranged from 7.3 ± 53.5 (millions of fish ± SD) to 1,751 ± 2,519. Estimates of abundance from the five range models produced similar results to the weighted arithmetic mean, ranging from 7.3 ± 53.5 (millions of fish ± SD) for the maximum range to 36.9 ± 247.0 for the minimum range.  These were generally considered more plausible than the results based on the geometric density means. Caveats to this abundance estimate are provided in the detailed document, but include considerations of the use of the lander dataset and the estimation of habitat area.  


### ROV minimum population estimate 

The ODFW has conducted remotely-operated vehicle (ROV) surveys for nearly 20 years, targeting nearshore rocky reef habitats and associated fish and invertebrate assemblages. Oregon ROV survey methods, analyses, and data were subjected to an SSC methodology review in 2019 and were determined to be suitable for use in west coast stock assessments, subject to assessment authors’ evaluation of suitability for particular stocks and specific data uses. Oregon ROV data were used to estimate a minimum abundance of quillback rockfish within a subset of the total available nearshore habitat, as a reference point for the assessment, though these data are not included directly in the assessment model. A summary of the methodology to develop this estimate follows, and a more detailed document is in development and available upon request by ODFW.  

ROV data from 2010 – 2019 were used for this abundance estimate, reflecting the period during which high-definition cameras were used. Sites were surveyed as funding and personnel allowed, and not all sites were surveyed in each year. Transect-level densities were aggregated by reef, regardless of year surveyed. Most transects were roughly 500m in length. These densities were derived from the rocky habitat portions of these transects only, excluding data from portions of transects over “soft” habitats (mud, sand, gravel). Total abundance (number of individuals) for the survey area was estimated by summing reef-level abundances. Each reef-level abundance was calculated as the weighted mean density of all transects conducted at the site across all years (weighted by the total view area of rock per transect) times the total area of mapped rock at the site within 20 – 70m range.

The total abundance estimate for quillback rockfish for the rock-only transect density expansion is 136,828 +/- 90,971 (SD) individuals. The total area included in this abundance estimate is 134.8 km2, representing an estimated 74.8% of total rocky habitat within 20 – 70m in Oregon waters. A total of 490 transects were included in the calculation of the site-level mean densities. Several regions of potential quillback rockfish habitat along the Oregon coast were not included in this estimate due to a lack of survey data. In the study’s 20 – 70m depth range, the most important of these is the coast south of Port Orford which holds over half of the remaining unsurveyed rocky reef area. Outside the study’s depth range, the most important missing rocky habitats are the shallows between 0 – 20m, which are typically difficult to survey using an ROV, and the expansive deeper (> 70m) portion of Arago Reef. Given these factors, the abundance estimate presented above is likely a minimum population estimate and intended to provide a reference point only for the scale of the population size in a portion of Oregon’s nearshore rocky habitat.

<!--chapter:end:54appendix.Rmd-->

