---
geometry: margin=1in
month: "`r format(Sys.Date(), '%B')`"
year: "`r format(Sys.Date(), '%Y')`"
preamble: |
output: sa4ss::techreport_pdf
bibliography: sa4ss.bib
lang: en
papersize: a4
---

```{r opts, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::knit_hooks$set(plot = function(x,options) {
      base = knitr::opts_knit$get('base.url')
      if (is.null(base)) base = ''
      alt = ifelse (is.null(options$alt),"",options$alt)
      cap = ifelse (is.null(options$caption),"",options$caption)
      if (alt != ""){
        sprintf('![%s](%s%s "%s")', cap, base, x, alt)
      } else {
        sprintf('![%s](%s%s)', cap, base, x)  
        }
  })

load("00opts.Rdata")

spp = 'quillback rockfish'
Spp = 'Quillback rockfish'
spp_latin = 'Sebastes maliger'

data_fig_loc = "//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/data/output biology/plots"

if(file.exists("00mod.Rdata")){
  load("00mod.Rdata")
} else {
  print("Model output not being read. Please run the read_model() function.")
}

```

<!--chapter:end:00a.Rmd-->

---
author:
  - name: Brian J. Langseth
    code: 1
    first: B
    middle: J
    family: Langseth
  - name: Chantel R. Wetzel
    code: 1
    first: C
    middle: R
    family: Wetzel
  - name: Jason M. Cope
    code: 1
    first: J
    middle: M
    family: Cope
  - name: Alison D. Whitman
    code: 2
    first: A
    middle: D
    family: Whitman
author_list: Langseth, B.J., C.R. Wetzel, J.M. Cope, A.D. Whitman
affiliation:
  - code: 1
    address: Northwest Fisheries Science Center, U.S. Department of Commerce, National
      Oceanic and Atmospheric Administration, National Marine Fisheries Service, 2725
      Montlake Boulevard East, Seattle, Washington 98112
  - code: 2
    address: Oregon Department of Fish and Wildlife, 2040 Southeast Marine Science
      Drive, Newport, Oregon 97365
address:
  - ^1^Northwest Fisheries Science Center, U.S. Department of Commerce, National Oceanic
    and Atmospheric Administration, National Marine Fisheries Service, 2725 Montlake
    Boulevard East, Seattle, Washington 98112
  - ^2^Oregon Department of Fish and Wildlife, 2040 Southeast Marine Science Drive,
    Newport, Oregon 97365
---

<!--chapter:end:00authors.Rmd-->

---
title: Status of Quillback Rockfish (_Sebastes maliger_) in U.S. waters off the coast of Oregon in 2021 using catch and length data
---

<!--chapter:end:00title.Rmd-->

\pagebreak
\pagenumbering{roman}
\setcounter{page}{1}

\renewcommand{\thetable}{\roman{table}}
\renewcommand{\thefigure}{\roman{figure}}

<!--chapter:end:01a.Rmd-->

\vspace{40cm}

_These materials do not constitute a formal publication and are for information only. They are in a pre-review, pre-decisional state and should not be formally cited (or reproduced). They are to be considered provisional and do not represent any determination or policy of NOAA or the Department of Commerce._

\pagebreak
\setlength{\parskip}{5mm plus1mm minus1mm}
\pagenumbering{arabic}
\setcounter{page}{1}
\renewcommand{\thetable}{\arabic{table}}
\renewcommand{\thefigure}{\arabic{figure}}
\setcounter{table}{0}
\setcounter{figure}{0}

\setlength\parskip{0.5em plus 0.1em minus 0.2em}

<!--chapter:end:10a.Rmd-->

# Introduction


## Basic Information

This assessment reports the status of `r spp` (*`r spp_latin`*) off the U.S. West Coast using data through `r endyr`. 

The stock off the Oregon coast was assessed as a separate stock from other populations off the U.S. West Coast based on the fairly sedentary nature of `r spp` which likely limits flow of fish to California and Washington [@HannahandRankin_rockfish_site_fidelity_2011; @Tolimierietal_rockfish_home_range_2009]. The substrate of the southern Washington coast is typically sandy bottom, which creates a natural separation between the Oregon and Washington populations. Additionally, the exploitation history and magnitude of removals off the Oregon coast differ from those in Washington and California.    


## Life History

`r Spp` are a medium- to large-sized nearshore rockfish found from southern California to the Gulf of Alaska [@loveetal_2002]. Off the U.S. West Coast `r spp` are primarily located north of central California, with rare observations south of Point Conception. 'r Spp' have historically been a part of both commercial and recreational fisheries throughout their range. 

`r Spp` are found in waters less than 274 meters in depth in nearshore kelp forests and rocky habitat [@loveetal_2002]. The diets of `r spp` consist primarily of benthic and pelagic crustaceans, and fish [@Murie_1995]. The body coloring or adult `r spp` is brown with yellow to orange blotching and light-colored dorsal saddle patches [@loveetal_2002]. As their name suggests, `r spp` have long dorsal fin spines.

Limited studies have been performed looking for genetic variation in `r spp` across the U.S. West Coast. Genetic work has revealed significant differences between Puget Sound and coastal stocks of `r spp` [@Seeb_geneflow_1998; @Stout_et_al_2001], however [@Seeb_geneflow_1998] did not find significant differentiation in populations of `r spp` between Washington and Alaska when Puget Sound samples were excluded. Significant population sub-division along the U.S. West Coast has been detected for the closely related, and more well-studied copper rockfish (*Sebastes caurinus*), indicating limited oceanographic exchange among geographically proximate locations [@Seeb_geneflow_1998; @buonaccorsi_population_2002; @johansson_influence_2008]. High site-fidelity [@HannahandRankin_rockfish_site_fidelity_2011] and relatively small home ranges [@Tolimierietal_rockfish_home_range_2009] for `r spp` suggests similar patterns of isolation-by-distance as found for other rockfish.

`r Spp` are a long-lived rockfish estimated to live up to 95 years [@loveetal_2002; @YamanakaandLacko_2001]. `r Spp` was determined to have a vulnerability (V = 2.22) of major concern in a productivity susceptibility analysis [@cope_approach_2011].  

## Ecosystem Considerations

Replace text if want to / have to include


## Historical and Current Fishery Information

`r Spp` off the coast of Oregon are primarily caught in both the commercial and recreational fisheries (Table \ref{tab:catch} and Figure \ref{fig:catch}). The landings from the commercial fishery extend back to 1892 and other than an increase in the late 1930s through the 1940s, were minimal until the late-1960s. Currently, `r spp` is one of several rockfish species targeted by a nearshore, primarily live-fish fixed gear fishery centered on Oregon’s southern coast. Following the development of the nearshore commercial fishery in the late 1990s, ODFW implemented a state-permitted limited access fishery that regulated fleet size, period landing limits and established harvest guidelines [@Rodomskyetal_2020). `r Spp` is one of 11 species in the Other Nearshore Rockfish category managed under a single state harvest guideline. Within this management category, China, quillback and copper rockfish are the three primary species landed. Landings from the recreational fishery off the coast of Oregon began in 1979 and removals from the recreational fleet have increased across time and now represent the majority of landings for `r spp` off the coast of Oregon. Recreational landings were large in the year that data were first available, and were expected to be minimal prior to the 1970s. Consequently a linear ramp in recreational landings was applied from 1970 to 1979.


## Summary of Management History and Performance

`r Spp` is managed by the Pacific Fishery Management Council (PFMC) as a part of the Nearshore Rockfish North and Nearshore Rockfish South complexes. The North and South complexes are split at N. 40$^\circ$ 10' Lat. N. off the U.S. West Coast. Each complex is managed based on a complex-level overfishing limit (OFL) and annual catch limit (ACL). The OFL and ACL values for the complexes are determined by summing the species specific OFLs and ACLs managed within each complex. Removals for species within each Nearshore complex are managed and tracked against the complex total OFL and ACL, rather than on a species by species basis.

`r Spp` was most recently assessed in 2010 using Depletion-Based Stock Reduction Analysis (DB-SRA) to provide estimates of coastwide OFLs ([@DickandMacCall_dbsra_2010]). The coastwide OFL was then apportioned to each management area based on the proportion of historical catches North and South of 40$^\circ$ 10' Latitude. DB-SRA does not assess overfished status, but assuming that current depletion was at the management target on average (e.g. 40%), the 2010 assessment found that `r spp` had a 52% chance of experiencing overfishing, in that recent coastwide catch of `r spp` slightly exceeded the median coastwide OFL estimate. 

The current OFL and ACLs for `r spp` North of 40$^\circ$ 10' Lat. N., the state/specific ACL allocation (58.4% for Oregon; Groundfish Management Team, pers. comm.), and the total removals are shown in Table \ref{tab:ofl}.

<!--chapter:end:11introduction.Rmd-->

# Data
The following types and sources of data were used in this assessment. Fishery catch and composition data were specific to Oregon, however biological data were estimated coastwide and included Oregon, Washington, and California sources. 

1. Commercial landings, and length, weight, and age data obtained from PacFIN and the Oregon Department of Fish and Wildlife (ODFW). Age compositions were not fit in the model. 
2. Estimates of commercial discard length frequencies and fraction discarded in the fishery obtained from the West Coast Groundfish Observer Program (WCGOP).
3. Recreational landings, discards, and length, weight, and age data obtained from RecFIN and the Oregon Department of Fish and Wildlife (ODFW). Age compositions were not fit in the model.
4. Fishery independent biological data (length, weight, and age) from the NWFSC WCGBTS survey.
5. Estimates of fecundity, maturity, and mortality from various sources.

A description of each data type is provided below, with timing of catch and composition data used in the base model shown in (Figure \ref{fig:data-plot}).

<!--chapter:end:20data.Rmd-->

## Fishery-Dependent Data

[Covid impacts??]

### Commercial Fishery

#### Landings

Historical commercial landings from 1892 to 1986 were provided by ODFW (Karnowski et al. 2014).  Historical landings were consistent but minimal (< 1 mt in all years except 1943) until the mid-1960s, at which point landings increased to a high of 3.5 mt in 1978. Primary gear types during this historical period included longline and troll gears. However, ODFW commercial samplers suggest that these troll landings were primarily landed on hook and line gear, but not separated by gear type on the fish tickets (pers. comm. M. Freeman, ODFW). 

Landings from 1987 – 1999 were compiled from a combination of PacFIN, the central repository for West coast commercial landings (extracted on 10/13/2020), and a separate ODFW reconstruction that delineated species-specific landings in the unspecified categories on PacFIN (e.g. URCK and POP1, ODFW 2017). Quillback rockfish landings from this reconstruction were substituted for the URCK and POP1 landings available from PacFIN, and added to PacFIN landings from other categories for a complete time series during this time period. Commercial landings from 2000 – 2020 are available on PacFIN (extracted on 10/13/2020 and 02/18/2021). `r Spp` is one of several rockfish species targeted by a nearshore, primarily live-fish fixed gear fishery centered on Oregon’s southern coast. `r Spp` are landed primarily with hook and line gear, but a substantial portion are also landed with bottom longline gear as well. On average, 94.2% of `r spp` landings are from these two gear types (2000 – 2020). In the most recent years, longline landings have eclipsed hook and line landings. Landings from all other gear types, including fish pot and trawl, are minimal relative to jig and longline gears and sporadic. Commercial landings for `r spp` increased from the mid-1960s to 1974 and have since fluctuated between approximately 0.4 and 4.5 mt annually. From 2003 to 2020, landings have averaged 1.6 mt annually, and represent approximately one third of the total removals. Commercial landings were aggregated across gear types into a single fleet in the base model. 

The input catches in the model represent total removals: landings plus discards (Table \ref{tab:catch} and Figure \ref{fig:catch}). Discards totals for the commercial fleet from 2002-2019 were determined based on West Coast Groundfish Observer Program (WCGOP) data provided in the Groundfish Expanded Mortality Multiyear (GEMM) product. The total coastwide observed discards in trawl and fixed gears were allocated by state and area based on the total observed landings observed by WCGOP. Discards were added to landings to obtain total removals for 2002-2019. Total removals prior to 2002, and for 2020 where no WCGOP data were yet available, were calculated based on the average coastwide discard rates of fixed gears from WCGOP of 5.7 percent. A fixed gear discard rate was used to better match the historical fleet as trawl catches and therefore discards were higher in the 2000s and lower previously.  

#### Length Compositions

Commercial quillback rockfish length samples are available from PacFIN from 1998 – 2020 (Table \ref{tab:com-len-samps}, extracted 2/23/2021). Approximately 44.3% of these samples are females (n = 1,361) and 54.2% are males (n = 1,664). There were 46 unsexed fish. The majority (77.2%) are from the southern Oregon coast, centered in Port Orford (65.3%) and Gold Beach (11.9%), where the majority of permit holders for the commercial nearshore fishery are based and where most of the landings are made. The majority of length samples are from `r spp` landed live (57.4%). Additionally, special projects length samples collected from the commercial fishery are available from PacFIN from 1999 – 2001, 2003 – 2006, 2008, 2010, 2012, 2015, and 2017 – 2019 (n = 210; extracted on 12/11/2020), but were not used due to concerns over non-random sampling.  

The distribution of the lengths in the commercial data ranged between 21 - 54 cm (the maximum length data bin size, Figure \ref{fig:com-len-data}). The mean size observed by the commercial fishery was relatively variable from year to year with the mean length occuring between 35 - 41 cm across both sexes (Figure \ref{fig:mean-com-len-data}) for all but the first two years, where mean length was 27 and 29 cm. 

The length observations in 1998 were not used in the base model due to very low (4) annual sample size. These data were used in the model as a 'ghost' fleet, not fit by the model but implied fits reflected in diagnostic plots. The implied fit to these data from the base model are shown in [Appendix B](#append_b).    

The input sample sizes for the commercial length data were calculated via the Stewart method (Ian Stewart, personal communication) which incorporate the number of trips and fish by year:

\begin{centering}

Input effN = $N_{\text{trips}} + 0.138 * N_{\text{fish}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $<$ 44

Input effN = $7.06 * N_{\text{trips}}$ if $N_{\text{fish}}/N_{\text{trips}}$ is $\geq$ 44

\end{centering}


### Recreational Fishery


#### Landings

_Historic Ocean Boat Landings (1979 – 2000)_

Recently, the Oregon Department of Fish and Wildlife (ODFW) undertook an effort to comprehensively reconstruct all marine fish recreational ocean boat landings prior to 2001 (pers. comm. A. Whitman, ODFW). Reconstructed catch estimates from the Oregon Recreational Boat Survey (ORBS) improve upon estimates from the federal Marine Recreational Fisheries Statistical Survey (MRFSS), which have known biases related to effort estimation and sampling [@VanVoorheesetal_2000] that resulted in catch estimates considered implausible by ODFW. However, the ORBS sample estimates are known to lack the comprehensive spatial and temporal coverage of MRFSS. Addressing this coverage issue is a major part of this reconstruction. In general, the base data and methodology for these reconstructed estimates are consistent with recent assessments for other nearshore species [@Dicketal_2016; @Dicketal_2018; @Haltuchetal_2018; @Copeetal_2019]. 

Prior to 2001, ORBS monitored marine species in both multi-species categories, such as rockfish, flatfish, and other miscellaneous fishes, and as individual species, such as lingcod or halibut. For this comprehensive reconstruction, four species categories were selected to reconstruct, including rockfish, lingcod, flatfish and miscellaneous, which constitute the bulk of the managed marine fish species. `r Spp` are a component of the rockfish species category. 

Category-level estimates were expanded to account for gaps in sampling coverage in two separate pathways. First, estimates from five major ports were expanded to include unsampled winter months in years lacking complete coverage. Expansions were based on available year-round sampling data and excluded years where regulations may have impacted the temporal distribution of catch.  Second, all other minor port estimates were expanded to include seasonal estimates in years lacking any sampling based on the amount of minor port catch as compared to all major port estimates. A subset of landings were sampled by ORBS for species compositions within these categories. Once category-level landings were comprehensive in space and time, species compositions were applied for the three multi-species categories, including rockfish, flatfish and miscellaneous fish. Borrowing rules for species compositions were specific to the category and determined based on a series of regression tree analyses that detailed the importance of each domain (year, month, port and fishing mode) to variability in compositions. 

Ocean boat estimates from 1979 – 2000 in numbers of fish of `r spp` from the above described methods were converted to biomass using biological samples from MRFSS (pers. comm. A. Whitman, ODFW). MRFSS biological data are available from 1980 – 1989 and 1993 – 2000. An annual average weight was applied to the total annual number of fish to obtain an annual landings estimate. Several years missing biological data (1979, 1990 – 1992) were filled in using neighboring years or interpolation. These landings in biomass were provided by ODFW and do not include an estimate of discarded fish. Landings during this time period gradually increased from 1979 to a peak of 7.1 mt in 1992, but fluctuated annually. Recreational landings were large in 1979, the year that data were first available, and were expected to be minimal prior to the 1970s. Consequently a linear ramp in recreational landings was applied from 1970 to 1979 for this assessment.   

_Modern Ocean Boat Landings (2001 – 2020)_

Recreational landings for ocean boat modes from 2001 – 2020 are available from RecFIN.  Both retained and released estimates of mortality are included, though retained mortality contributes the vast majority to total mortality. Release mortality is estimated from angler-reported release rates and the application of discard mortality rates from the PFMC.  From 2001 – 2020, landings averaged 4.6mt, ranging from 0.7 to 9.5 mt. In 2020, ocean boat landings were 6.3 mt.

_Shore and Estuary Landings (1979 – 2020)_

ODFW provided reconstructed estimates of shore and estuary landings for `r spp` from 1979 – 2020, using methodology similar to recent assessments [@Bergeretal_2015, @Dicketal_2018, @Copeetal_2019]. Data sources include MRFSS and the Oregon Shore and Estuary Boat Survey (SEBS). Numbers of fish were provided by MRFSS from 1980 – 1989 and 1993 – June 2003, and by SEBS from July 2003 – June 2005. An annual mode-specific average weight was applied to numbers of `r spp` from 1980 – 1989 and 1993 – 2005. Separate weights were calculated for shore and estuary boat modes, and excluded extreme outliers and imputed values. This reconstruction also applied two scaling factors to remove bias towards freshwater sampling and underestimation of estuary boats, as detailed in [@Dicketal_2018]. To estimate quillback rockfish landings from July – December 2005, an expansion was developed using the three year average of the ratio between the first six months of the year and the total annual landings from MRFSS and SEBS landings from 2002 - 2004. Separate expansions were developed for shore mode and estuary boat modes. A three year average (1980 - 1982) was used to estimate shore and estuary boat landings for 1979.  

The ODFW does not currently sample shore and estuary boat fishing trips, and so a 10 year average landing (1996 – 2005; 0.024 mt/year) was used to estimate shore and estuary boat landings during 2006 – 2020. Shore and estuary boat landings for quillback rockfish were sporadic. Shore and estuary boat landings averaged 0.07 mt annually from 1980 – 2003.

Recreational removals were aggregated across modes into a single fleet in the model (Table \ref{tab:catch} and Figure \ref{fig:catch}). Values from 2001-2020 represent total removals consisting of both landings and estimated discard mortality. No recreational discarding was assumed for the years 2000 and prior, because the bag limits (15 fish bag limit) are thought to not have been restrictive enough to induce appreciable size based discarding of `r spp`.

#### Length Compositions

Recreational length samples were obtained from two sources: MRFSS and RecFIN (ORBS). From 1980 – 1989 and from 1993 – 2000, the MRFSS program collected samples from both ocean and inland (estuary) areas. ODFW provided MRFSS samples with the addition of a column that flagged length values imputed from weights to allow for selection of directly measured values; however, sample size was limited and therefore, imputed lengths were used.  From 1980 – 1989, total lengths (mm) were collected by MRFSS, which were converted to fork length. From 1993 – 2000, fork length (mm) was collected. Length samples from 2001 – 2020 from the ORBS sampling program are available on RecFIN. All ORBS samples are by fork length (mm). The vast majority (78%) of these samples are from ocean trips, or do not distinguish inland from ocean (21%). Special projects samples collected by ODFW staff from the recreational fishery are also available from 1998 – 2001 and 2013 - 2015 (n = 150), but were not used due to concerns about non-random sampling. Table \ref{tab:len-samps} details sample sizes used by year in the base model. Retention of `r spp` was not allowed under recreational state regulations in 2015 or 2016, limiting the number of samples in those years. Furthermore, released samples (n = 121), of which 60 occurred in 2015 and 2016, were not used in length compositions for the base model.   

The distribution of the lengths in the recreational data ranged between 20 - 54 cm (the maximum length data bin size, Figure \ref{fig:rec-len-data}). The mean length by year in the recreational data was more variable prior to 2000, after which the mean lengths observed by year became relatively stable with tight 95 percent confidence intervals (Figure \ref{fig:mean-rec-len-data}).

The input sample sizes for the recreational length data were calculated equal to the number of length samples available by year. 

<!--chapter:end:21f-.Rmd-->

## Fishery-Independent Data

No fishery-independent data sources that are commonly incorporated in West Coast groundfish assessments (as required by the data moderate Terms of Reference) had adequate sample size of `r spp` off the Oregon coast to include abundance indices for this assessment. The WCGBTS, and historically the Triennial survey, collect data off the Oregon Coast on rockfish biology and abundance. There were no more than ten positive tows of `r spp` in any one year coastwide in the WCGBTS, but typically fewer than five. Similarly there were no more than five positive tows of `r spp` in any one year coastwide for the Triennial survey. Biological data from the WCGBTS surveys were used in external calculations of biological parameters. No ages or weights for 'r spp' were available from the Triennial survey. 

Oregon has a number of state-specific small-scale fishery-independent surveys considered by ODFW to have adequate samples of `r spp`. These include....Given these surveys are not commonly incorporated into West Coat groundfish assessments, and are not explicitly conducted as a state-wide estimate of relative or absolute abundance, we do not include the data in the model for `r spp`. However, we do compare estimates from these surveys to the our assessment model in Section \ref{Unresolved-Problems-and-Major-Uncertainties}. 

<!--chapter:end:21s-.Rmd-->

### \acrlong{s-wcgbt}

Information from the West Coast Groundfish Bottom Trawl Survey (WCGBTS) was used to calculate biological parameters including growth and weight-at-length relationships. An index of abundance was not calculated due to small sample size, and consequently, length composition data was not included in the model. 

The WCGBTS is based on a random-grid design; covering the coastal waters from a depth of 55-1,280 m [@bradburn_2003_2011]. This design generally uses four industry-chartered vessels per year assigned to a roughly equal number of randomly selected grid cells and divided into two 'passes' of the coast. Two vessels fish from north to south during each pass between late May to early October. This design therefore incorporates both vessel-to-vessel differences in catchability, as well as variance associated with selecting a relatively small number (approximately 700) of possible cells from a very large set of possible cells spread from the Mexican to the Canadian borders.

<!--chapter:end:21s-wcgbts.Rmd-->

## Biological Data

### Natural Mortality

Hamel [-@hamel_method_2015] developed a method for combining meta-analytic approaches relating instantaneous natural mortliaty rate ($M$) to other life-history parameters such as longevity, size, growth rate, and reproductive effort to provide a prior on $M$. Then et al. [-@then_evaluating_2015-1] provided an updated data set of estimates of $M$ and related life history parameters across a large number of fish species from which to develop an $M$ estimator for fish species in general. They concluded by recommending $M$ estimates be based on maximum age alone, based on an updated Hoenig non-linear least-squares estimator $M=4.899A^{-0.916}_{max}$. The approach of basing $M$ priors on maximum age alone was one that was already being used for West Coast rockfish assessments. However, in fitting the alternative model forms relating $M$ to $A_{\text{max}}$, Then et al. [-@then_evaluating_2015-1] did not consistently apply their transformation. In particular, in real space, one would expect substantial heteroscedasticity in both the observation and process error associated with the observed relationship of $M$ to $A_{\text{max}}$. Therefore, it would be reasonable to fit all models under a log transformation. This was not done. Re-evaluating the data used in Then et al. [-@then_evaluating_2015-1] by fitting the one-parameter $A_{\text{max}}$ model under a log-log transformation (such that the slope is forced to be -1 in the transformed space Hamel [-@hamel_method_2015]), the point estimate for $M$ is:

\begin{centering}

$M=\frac{5.4}{A_{\text{max}}}$

\end{centering}

The above is also the median of the prior suggested by Hamel [-@hamel_method_2015]. The prior is defined as a log normal distribution with parameters $\mu = ln(5.4/A_{\text{max}})$ and $\sigma = 0.438$. Using a maximum age of `r model$accuage` years, the point estimate and median of the prior for $M$ is `r model$parameters["NatM_p_1_Fem_GP_1","Value"]` per year.

The maximum age was selected based on literature values for the U.S. West Coast examining the longevity of `r spp` [@loveetal_2002; @Palssonetal_1999; @Yamanaka_and_Lacko_2001]. The oldest aged `r spp` among available data used in the assessment was 70 years with two observations off the coast of Washington in 1999.   


### Maturation and Fecundity
Maturity-at-length estimates were based on the work of Hannah and Blume [-@Quillback_maturity_2011] which estimated the 50% size-at-maturity of `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm and slope of `r round(model$MGparmAdj$Mat_slope_Fem_GP_1[1], 2)` off the coast of Oregon with maturity asymptoting to 1.0 for larger fish (Figure \ref{fig:maturity}). A length at 50% maturity of `r round(model$MGparmAdj[,"Mat50%_Fem_GP_1"][1], 1)` cm is consistent with other studies for `r spp`, which range 26-32 cm (see Jason's life history matrix).  

The fecundity-at-length was based on research by Dick et al. [-@dick_meta-analysis_2017]. The fecundity relationship for `r spp` was estimated equal to `r format(model$MGparmAdj$Eggs_scalar_Fem[1], scientific = TRUE)`$L$^`r round(model$MGparmAdj$Eggs_exp_len_Fem[1],2)`^ in millions of eggs where $L$ is length in cm. Fecundity-at-length is shown in Figure \ref{fig:fecundity}.


### Sex Ratio
This assessment modeled `r spp` as a single sex. Data available were generally sparse, growth and length-weight relationships were similar across sexes, and the literature provided limited evidence of sexual dimorphism in length [@LenarzandEcheverria_dimorphism_1991]. As such, the sex ratio was assumed to be 1:1. There was limited sex specific observations by length or age for all biological data sources (Figures \ref{fig:len-sex-ratio} and \ref{fig:age-sex-ratio}).


### Length-Weight Relationship
The length-weight relationship for `r spp` was estimated outside the model using available coastwide biological data collected from fishery-independent and fishery-dependent data sources (Figure \ref{fig:len-weight-survey}). Sources included the WCGBT and Triennial Surveys, and recreational and commercial samples from all states. Only measured weight or length values were used; any values with more than two decimal places were assumed to be calculated from another measurement and were excluded. This occurred for 32 percent of lengths and 20 percent of the weights in the MRFSS-era recreational samples. The estimated length-weight relationship for `r spp` was `r format(model$MGparmAdj$Wtlen_1_Fem[1], scientific = TRUE)`$L$^`r round(model$MGparmAdj$Wtlen_2_Fem[1],2)`^ where $L$ is fork length in cm (Figures \ref{fig:len-weight}).


### Growth (Length-at-Age)
The length-at-age relationship for `r spp` was estimated outside the model using data collected from fishery-dependent sources off the coast of Oregon and Washington collected between 1998-2019, and from a single coastwide fishery-independent sources (WCGBT Survey) collected between 2005-2019 (Table \ref{tab:len-at-age-samps}).  Age data was generally sparase for `r spp` from any one source. The fishery-dependent data had limited observations of young fish less than 5 years of age, but had observations of fish up to 73 years of age, and the fishery-independent data had limited observations of old fish greater than 40 years of age, but had observations of fish as young as one year of age. Growth parameters for `r spp` were estimated at the following values:

\begin{centering}

$L_{\infty}$ = `r round(model$MGparmAdj$L_at_Amax_Fem_GP_1[1], 1)` cm; $k$ = `r round(model$MGparmAdj$VonBert_K_Fem_GP_1[1], 3)`

\end{centering}

These values were fixed within the base model. The coefficient of variation (CV) around young and old fish was fixed at a value of 0.10 for both sexes. The length-at-age curve with the CV around length-at-age is shown in Figure \ref{fig:len-age-ss}.  
  
  
### Ageing Precision and Bias
Ages were not fit in the model. 

<!--chapter:end:22biology.Rmd-->

# Assessment Model

## Summary of Previous Assessments 

`r Spp` was last assessed in 2010 ([@DickandMacCall_dbsra_2010]). The stock was assessed using Depletion-Based Stock Reduction Analysis (DB-SRA) which is a data-limited approach that incorporates catch data with priors on select parameters natural mortality, the ratio of fishing mortality at maximum sustainable yield to natural mortality, current depletion, and the depletion at maximum sustainable yield to estimate overfishing status, but not overfished status. `r Spp` was assessed as a single coastwide stock to generate an overall OFL that was then apportioned to each management area based on the proportion of historical catches North and South of 40$^\circ$ 10' Lat. N.. Assuming that current depletion was at the management target on average (e.g. 40%), the 2010 assessment found that `r spp` had a 52% chance of experiencing overfishing coastwide. 

### Bridging Analysis

A direct bridging analysis was not conducted because the previous assessment was structured as a single coastwide model. The previous assessment also used DB-SRA, which uses different assumptions and data than the model used for this assessment, making a bridging analysis intractable.  


## Model Structure and Assumptions

The Oregon `r spp` area was assessed using a one-sex model with life history parameters combined across sexes. The model assumed two fleets: 1) commercial and 2) recreational fleets with removals beginning in `r startyr`. Selectivity for the commercial fleet was specified to be asymptotic using the six-parameter double normal parameterization within SS. The ascending width and beginning size of maximum selectivity parameters were estimated for the commercial fleet. The recreational fleet also used the six-parameter double normal parameterization with the ascending width and beginning size of maximum selectivity parameters estimated, but also was allowed to estimate reduced selectivity for the largest fish (i.e., allowed to be dome-shaped). Annual recruitment deviations were estimated within the base model.

### Modeling Platform and Structure

Stock Synthesis (SS) version 3.30.16 was used to estimate the parameters in the model. The R package r4ss, version 1.41.0, along with R version 4.0.2 were used to investigate and plot model fits. The NWFSC developed R packages nwfscSurvey_2.0 and PacFIN.Utilities_0.0.2.0000 were used for synthesis and processing of data for use in Stock Synthesis. 

### Priors

Priors were used with fixed parameter values for natural mortality and steepness in the base model.  The prior distribution for natural mortality was based on the Hamel [-@hamel_method_2015] meta-analytic approach with an assumed maximum age of 90 years. The prior assumed a lognormal distribution for natural mortality with a median of 0.06 and a standard deviation of 0.48. 

The prior for steepness assumed a beta distribution with mean of 0.72 and standard deviation of 0.158. The prior parameters are based on the Thorson-Dorn rockfish prior (commonly used in past West Coast rockfish assessments) conducted by James Thorson (personal communication, NWFSC, NOAA) which was reviewed and endorsed by the Scientific and Statistical Committee (SSC) in 2017. However, this approach was subsequently rejected for future analysis in 2019 when the new meta-analysis resulted in a mean value of approximately 0.95. In the absence of a new method for generating a prior for steepness the default approach reverts to the previously endorsed method, the 2017 value.

### Data Weighting

Length composition data for the comercial fishery started with a sample size determined from the equation listed in Sections \ref{commercial-fishery}. The input sample size for the recreational fishery length composition data was set equal to the number of length samples by year.   

The base  model was weighted using the "Francis method", which was based on equation TA1.8 in Francis [-@francis_data_2011]. This formulation looks at the mean length or age and the variance of the mean to determine if across years, the variability is explained by the model. If the variability around the mean does not encompass the model predictions, then that data source should be down-weighted. This method accounts for correlation in the data (i.e., the multinomial distribution). Sensitivities were performed examining the difference in weighting using McAllister-Ianelli Harmonic Mean Weighting[-@mcallister_bayesian_1997] and the Dirichlet Multinomial Weighting [-@thorson_model-based_2017].

### Estimated and Fixed Parameters

There were `r tail(model$parameters$Active_Cnt,1)` estimated parameters in the base model. These included one parameter for $R_0$, 5 parameters for selectivity, 71 recruitment deviations, and 12 forecast recruitment deviations (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`, and natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)`, as described above in Section \ref{Priors}. Growth, maturity-at-length, and length-at-weight were fixed as described above in Section \ref{data}. The standard deviation of recruitment deviates was fixed at `r round(model$parameters[model$parameters$Label == "SR_sigmaR","Value"],2)`. Sensitivity analyses and likelihood profiles were performed for steepness, natural mortality, length at maximum size, and vonBertalanffy growth coefficient. 

Dome-shaped selectivity was explored for all fleets within the model. Older `r spp` are often found in deeper waters and may move into areas that limit their availability to fishing gear. Dome shaped selectivity can also occur under hetergenous fishing pressure [sampson]

[Ali provide justification for dome shape for the rec fleet]

The final base model estimated dome-shaped selectivity for the recreational fishery. The selectivty for the commercial fishery was fixed as asymptotic. During initial model development, the descending width and width of maximum selectivity parameters for the recreational and commercial fleets were estimated to identify appropriate fixed values consistent with the data, and then fixed at those estimates. 


## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the Oregon coast. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.


<!--chapter:end:30model.Rmd-->

## Summary of Previous Assessments and Reviews


### History of Modeling Approaches (not required for an update assessment)


### Most Recent STAR Panel and SSC Recommendations (not required for an update assessment)


### Response to Groundfish Subcommittee Requests (not required in draft)

<!--chapter:end:31summary.Rmd-->

## Base Model Results

The base model parameter estimates along with approximate asymptotic standard errors are shown in Table \ref{tab:params} and the likelihood components are shown in Table \ref{tab:likes}. Estimates of derived reference points and approximate 95 percent asymptotic confidence intervals are shown in Table \ref{tab:referenceES}. Estimates of stock size and status over time are shown in Table \ref{tab:timeseries}.

### Parameter Estimates

Estimated parameter values are provided in Table \ref{tab:params}. The $R_0$ was estimated at `r round(model$parameters[model$parameters$Label == 'SR_LN(R0)', 'Value'], 2)`. The selectivity curves for the commercial and recreational fleet are shown in Figure \ref{fig:selex}. The selectivity was fixed to be asymptotic for the commercial fleet with a peak in maximum selectivity for fish starting at `r round(model$parameters[model$parameters$Label == 'Size_DblN_peak_OR_Commercial(1)', 'Value'], 1)` cm. The selectivity for the recreational fleet was estimated to be dome-shaped at the largest sizes. The peak of the selectivity curve by the recreational fleet was estimated to start at `r round(model$parameters[model$parameters$Label == 'Size_DblN_peak_OR_Recreational(2)', 'Value'], 1)` cm and decline at `r round(model$parameters[model$parameters$Label == 'Size_DblN_peak_OR_Recreational(2)', 'Value'], 1) + exp(round(model$parameters[model$parameters$Label == 'Size_DblN_peak_OR_Recreational(2)', 'Value'], 1))/(1+exp(round(model$parameters[model$parameters$Label == 'Size_DblN_peak_OR_Recreational(2)', 'Value'], 1))) ` cm. Sensitivities to the shape and potential time blocking of the recreational selectivity was explored (see [Sensitivies](#sensitivites) for details). After discussions with individuals knowledgable about the recreational fishery, we theorized that the limited dome-shape in selectivity could arise due to 

[Ali add in information]

The estimated annual recruitment and recruitment deviations are shown in  Figures \ref{fig:recruits} and \ref{fig:rec-devs}. Strong recruitment events were estimated to have occurred in 1995 and 1999 and 2012 which resulted in a substantial increase in biomass during the late 1990s and early to mid 2000s. While the largest recruitment deviations were estimated to have occurred in these three specific years, the surrounding years in the 1990s also have above average recruitment estimated, whereas the surrounding years in the 2000s have lower than average recruitment estimated. The 1995 and 1999 large recruitment pulses show up in the composition data for both the commercial and recreational fleets not as a dramatic pulse of young fish but more as a steady increasing trend in mean size that help contribute to the increasing catches over the time given the estimates of population size. The steadily increasing mean size in the recreational fleet along with minimal catches of smaller fish in the compositional data supports the below average recruitment in the 2000s, until 2012. The 2012 large recruitment pulses show up in the composition data for both the commercial and recreational fleets as pulses of smaller fish that are also reflected by declines in mean size. Bias adjustment was applied to the annual estimates of recruitment deviations following the pattern of increased bias adjust for recent years as shown within r4ss (Figure \ref{fig:bias-adj}). 

### Fits to the Data

Fits to the length data are shown based on the Pearson residuals-at-length, the annual mean lengths, and aggregated length composition data for the commercial and recreational fleets. The Person residuals for the commercial fishery have no discernible pattern of misfit to the length data across cohorts but show areas of misfit over time (Figure \ref{fig:com-pearson}). The residuals show that the peak of the composition is being underfit for many years. These years have lower sample size, and for years with high sample size such as 2000, 2002, and 2017, compositions are being fit well. The largest residuals were observed within sparse years (1998) or when missing small spikes of small fish in the compositions (2009, 2017, 2020) (see [Appendix A](#append_a) for details). The mean lengths observed by the commercial fishery were variable by year with consistent confidence intervals and showed an increase in mean length followed by a period of stability and then decline (Figure \ref{fig:com-mean-len-fit}). 

[could apply block around 2003 and cut comps prior to 2000]
[maybe even remove commercial comps and show the effect is minimal]

The Pearson residuals for the recreational length data are variable by year have no discernible pattern of misfit to the length data (Figure \ref{fig:rec-pearson}). A period of positive residuals from 2005-2014 show that the peak of the composition is being slightly underfit, however looking at the fits suggest overall good fit (see [Appendix A](#append_a) for details). The residual patterns for 2017-2020, which are the largest residuals outside extreme lengths in low sample size years, show the model has difficulty fitting the bimodal patterns in these years, which are not unexpected. Throughout the mid-2000s the mean length increases to a larger size (around 40 cm in 2015) with a substantial decrease in variation of the observed lengths compared to pre-2000 lengths (Figure \ref{fig:rec-mean-len-fit}). The mean length was highly variable in 2015 due to low sample size (Table \ref{tab:len-samps}) 

Detailed fits to the length data by year are provided in [Appendix A](#append_a). Aggregate fits by fleet are shown in Figure \ref{fig:agg-len-fit}. The model fits the aggregated lengths for the recreational fleet well. The fit to the commercial fleet is poorer. Both fleets show similar ranges of sizes caught and an aggregated peak around 40 cm. The commercial fleet shows proportionally less catch of intermediate size fish between 30-40 cm compared to the recreational fleet. The model overfits the proportion of intermediate fish in the commercial fishery and underestimates the proprotion of fish selected at their peak.

[explain the pattern from comercial gear does not appear to be due to differences in gear - its common across most gears]

[The poor fit to the commerical aggregate lengths was further explored with sensitivites on applying selectivity blocks to the commercial fleet. The differences on overall model results were small, and with lack of clear evidence for blocks within the commercial fleet, and added complexity with applying blocks, we chose to not include in the base model]

### Population Trajectory

The predicted spawning output (in millions of eggs) is given in Table \ref{tab:timeseries} and plotted in Figure \ref{fig:ssb}. The predicted spawning output from the base model declines until around the year 1995, steadies due to several above average recruitment events that occurred in the mid- to late-1990s. The population then increases dramatically in the early 2000s due to the very large recruitment event in 1994. The population increase slows in the late 2000s, and then declines in the 2010s due to below average recruitment through the 2000s. The estimate of total biomass over time is shown in Figure \ref{fig:tot-bio}.

The `r endyr` spawning output relative to unfished equilibrium spawning output is above the target of 40 percent of unfished spawning output (`r round(model$derived_quants[model$derived_quants$Label == 'Bratio_2021','Value'], 2)`, Figure \ref{fig:depl}). Approximate confidence intervals based on the asymptotic variance estimates show that the uncertainty in the estimated spawning output is large ranging between approximately 25 - 75 percent of unfished equilibrium spawning output. 

[ need to do the follow and check]

The slight dome shape in the final selectivity for the recreational fleet results in a small fraction of large fish that unavailable in recent years (Figure \ref{fig:unavail-bio}). The fraction of large fish unavailable is relatively small portion of the overall biomass and in theory would be available for selection from the commercial fishery.   

The stock-recruit curve resulting from a value of steepness fixed at `r print(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)` is shown in Figure \ref{fig:bh-curve}.

### Reference Points

Reference points were calculated using the estimated selectivity and catch distributions among fleets in the most recent year of the model (`r endyr`, Table \ref{tab:referenceES}). Sustainable total yields  were `r round(model$derived_quants[model$derived_quants$Label == 'Dead_Catch_SPR', 'Value'], 2)` mt when using an $SPR_{50\%}$ reference harvest rate. The spawning output equivalent to 40 percent of the unfished spawning output ($SB_{40\%}$) was `r round(model$derived_quants[model$derived_quants$Label == 'SSB_SPR', 'Value'], 2)` millions of eggs. 

The `r endyr` spawning output relative to unfished equilibrium spawning output is above the target of 40 percent of unfished spawning output (Figure \ref{fig:depl}). The fishing intensity, $1-SPR$, has been above the harvest rate limit ($SPR_{50\%}$) from 1978-2005, and in all but two years since 2010 (Table \ref{tab:timeseries} and Figure \ref{fig:1-spr}). Table \ref{tab:referenceES} shows the full suite of estimated reference points for the base model and Figure \ref{fig:yield} shows the equilibrium curve based on a steepness value fixed at `r model$parameters[model$parameters$Label == "SR_BH_steep","Value"]`.

<!--chapter:end:33results.Rmd-->

## Model Diagnostics
Describe all diagnostics

### Convergence

Proper convergence was determined by starting the minimization process from dispersed values of the maximum likelihood estimates to determine if the model found a better minimum and adjusting phases of the estimated parameters. Starting parameters were jittered by 10 percent. This was repeated 100 times with 10 out of 100 runs returned to the base model likelihood. A better, lower negative log-likelihood, model fit was not found. The model did not experience convergence issues when provided reasonable starting values. Through the jittering done as explained, likelihood profiles, and alternative phasing, we are confident that the base model as presented represents the best fit to the data given the assumptions made. There were no difficulties in inverting the Hessian to obtain estimates of variability throughout initial model attempts and all explorations resulted in a positive-definite Hessian. 

### Sensitivity Analyses

A number of sensitivity analyses were conducted.  The majority of the sensitivities conducted was a single exploration from the base model assumptions and/or data, and were not performed in a cumulative fashion.

\begin{enumerate}
   
  \item Deterministic recruitment from the stock recruitment curve. 

  \item Data weighting according to the McAllister-Ianelli method (MI DW) using the weighting values shown in Table \ref{tab:dw}. 
  
  \item Data weighting according to the Dirichlet Multinomial method (DM DW) where the estimated parameters are shown in Table \ref{tab:dw}. 

  \item Estimate $L_{\infty}$.
  
  \item Estimate $L_{\infty}$ and $k$.

  \item Estimate the coefficient of variation for older fishes.

  \item Estimate natural mortality.
  
  \item Exclude spare composition data for the commercial and recreational fleets

  \item Fix recreational selectivity form to be asymptotic. 
  
  \item Fix commercial selectivity form to be dome-shaped.

  \item Estimate recreational selectivity block: 1979-1999 with asymptotic selectivity curve and 2000-2020 with dome-shaped selectivity.   
  
  \item Separate genders and model as two-sex model.
  
\end{enumerate}

Likelihood values and estimates of key parameters from each sensitivity are available in Table \ref{tab:sensitivities}. Plots of the estimated time-series of spawning biomass and relative spawning biomass are shown in Figures \ref{fig:sens-ssb} and \ref{fig:sens-depl}.

The largest change from the base model resulted when recruitment was fixed to be deterministic.  The sensitivity estimated a higher stock scale and a less depleted stock relative to the base model. Assuming asymptotic selectivity for the recreational fleet resulted in a reduction in the scale and status of the stock. The sensitivity that used all recreational length data and estimated two time blocks for selectivity estimated similar final stock status and size compared to the base model.

Data weighting with the McAllister-Ianelli (MI) resulted in a similar stock trajectory to the base model, however, the Diricthlet-Multinomial (DM) increased the variability in the stock trajectory (slightly higher high and lower low) with a final stock status less depleted than the base model. Estimating single life history parameters, the CV at older ages or female natural mortality, were similar to the base model. In contrast, estimating the $L_{\infty}$ for both sexes resulted in a more pessimistic view of the final stock status compared to the base model. 

### Likelihood Profiles

Likelihood profiles were conducted for $R_0$, steepness, natural mortality, $L_{\infty}$, and growth coefficient ($k$) values separately. These likelihood profiles were conducted by fixing the parameter at specific values and estimating the remaining parameters based on the fixed parameter value. 

In regards to values of $R_0$, the negative log-likelihood was minimized at approximately a log($R_0$) of `r round(log(model$derived_quants[model$derived_quants$Label == "Recr_Virgin",2]),2)` (Figure \ref{fig:r0-profile}). Both the commercial and recreational data supported lower log($R_0$) values. Increasing the $R_0$, relative to the value estimated, results in an a sharp increase in stock scale and status (Figure \ref{fig:r0-ssb} and \ref{fig:r0-depl}). 

For steepness, values from approximately 0.30 to 1.0 were supported with the lowest negative log-likelihood occurring at the upper bound of 1.0 (Figure \ref{fig:h-profile}). Assuming higher or lower steepness values had minimal impact on the unfished and spawning output estimated (Figure \ref{fig:h-ssb}). The estimated relative final stock status was generally within the pre-cautionary zone, between 0.25 and 0.40  of unfished, across steepness values except for the lowest steepness values (0.30 and 0.40) (Figure \ref{fig:h-depl}).

The negative log-likelihood profile across female natural mortality supported values between 0.105 and 0.125 which included the fixed value of `r model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"]` (Figure \ref{fig:m-profile}). The estimated stock trajectories assuming lower or higher natural mortality values impacted the estimated unfished spawning output and resulted in stock statuses just below or within the management precautionary zone (between 0.25 - 0.40) and above (Figures \ref{fig:m-ssb} and  \ref{fig:m-depl}). 

A profile across a range of female $L_{\infty}$ values was also conducted (Figure \ref{fig:linf-profile}).  The negative log-likelihood showed support for values between 47.5 and 48.5 cm. The $L_{\infty}$ value for female fish in the model was fixed at `r model$parameters[model$parameters$Label == "L_at_Amax_Fem_GP_1","Value"]`. The stock scale and status is quite variable across alternative $L_{\infty}$ values where assuming lower values resulted in sharp increases in stock scale and status (Figures \ref{fig:linf-ssb} and \ref{fig:linf-depl}).

A profile across a range of female $k$ values was also conducted (Figure \ref{fig:k-profile}).  The negative log-likelihood showed support for values between 0.17 and 0.22. The $k$ value for female fish in the model was fixed at `r model$parameters[model$parameters$Label == "VonBert_K_Fem_GP_1","Value"]`. The stock scale and status increases under lower $k$ values where assuming higher values resulted in decreases in stock scale and status (Figures \ref{fig:k-ssb} and \ref{fig:k-depl}).

### Retrospective Analysis

A five-year retrospective analysis was conducted by running the model using data only through 2015, 2016, 2017, 2018, 2019 and 2020. The estimated spawning output was generally consistent with the base model when recent years of data were removed (Figures \ref{fig:retro-ssb} and \ref{fig:retro-depl}).  Removing the final 3 - 5 years of data resulted in a decline is spawning output relative to the base model likely due to the limited length samples from the recreational fishery available in 2015 and 2016 when retention was prohibited in the Oregon recreational fishery. 


### Unresolved Problems and Major Uncertainties

Rec patterns

Growth

Dome-shaped selectivity

<!--chapter:end:34diagnostics.Rmd-->

# Management 

## Harvest Projections and Decision Tables

A ten year projection of the base model with catches equal to the estimated Acceptable Biological Catch (ABC) based on the category 2 time-varying and $P^*$ = 0.45 for years 2023-2032 (Table \ref{tab:project}). The removals in 2021 and 2022 were set based on the adopted Annual Catch Limits (ACLs) and the percent allocation (49 percent) for Oregon provided by the PFMC Groundfish Management Team (GMT, personal communication). 

The decision table uncertainty axes and catch levels are to be determined later.

## Evaluation of Scientific Uncertainty

The estimated uncertainty in the base model around the `r endyr + 1` spawning output is $\sigma$ = `r round(model$Pstar_sigma,2)` and the uncertainty in the base model around the `r endyr + 1` OFL is $\sigma$ = `r round(model$OFL_sigma,2)`. The estimated model uncertainty was less than the category 2 groundfish data moderate assessment default value of  $\sigma$ = 1.0. 

## Research and Data Needs

The ability to estimate additional process and biological parameters for `r spp` was limited by data.  Collecting the following data would be beneficial to future assessments of the stock:

\begin{itemize}

	\item Continue collecting length and otolith samples from recreational catches.

	\item The recreational selecitivity form was a source of uncertainty in the base model. Improved understanding of where recreational fishing is commonly occuring (areas and depths) and the range of sizes available by depth would be beneficial to better understand the selectivity form.  
	
	\item Recruitment patterns showed lower than average recruitment in the 2000s. Additional evidence to support patterns in recruitment would support recruitment estimates.  
	
	\item The presence of 'r spp' in standard fishery-independent surveys was too sparse to include as indices of abundance. Fishery-independnt surveys specific to quillback rockfish would help with understanding population trends. 
	
\end{itemize}

Fishery-independent surveys along the Oregon coast have been conducted by the ODFW. 

[more info on Oregon surveys]

<!--chapter:end:40management.Rmd-->

# Acknowledgments
Many people were instrumental in the successful completion of this assessment and their contribution is greatly appreciated. We are very grateful to all the agers at WDFW, ODFW, and the CAP lab for their hard work reading numerous otoliths and availability to answer questions when needed. Jason Jannot and Kayleigh Sommers assisted with data from the WCGOP and entertained our many questions. We would like to acknowledge our survey team and their dedication to improving the assessments we do. Peter Frey and John Harms were incredibly helpful in facilitating the understanding of the STAT team as to why and when each of our assessments either encounter or do not quillback rockfish along the coast.

Melissa Head provided an area specific maturity estimate for quillback rockfish and provided insight in the complex biological processes that govern maturity processes.

All of the data moderate assessments this year were greatly benefited by the numerous individuals who took the time to participate in the pre-assessment data webinar. Gerry Richter, Merit McCrea, Louis Zimm, Bill James, and Daniel Platt were provided insight to the data and the complexities of the commercial and recreational fisheries off the West Coast of the U.S. which were essential in the production of all of the quillback rockfish assessments conducted this year.

<!--chapter:end:41acknowledgments.Rmd-->

\clearpage

# References
<!-- If you want to references to appear somewhere before the end, add: -->
<div id="refs"></div>
<!-- where you want it to appear -->
<!-- The following sets the appropriate indentation for the references
  but it cannot be used with bookdown and the make file because it leads
  to a bad pdf.
\noindent
\vspace{-2em}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
 -->

<!--chapter:end:49bibliography.Rmd-->

\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

<!-- tab:catch -->
\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/Catches_All_Years.tex}

\newpage


```{r, results = 'asis'}
yrs = hist = 2011:2020
nfleets = 2
catch = dead = total.dead = 0
for (i in 1:nfleets){
  name = paste0("retain(B):_",i)
  input.catch = model$timeseries[model$timeseries$Yr %in% yrs, name]
  catch = cbind(catch, input.catch)
}
total.catch <- round(apply(catch, 1, sum),2)

man = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")
man = man[man$Year %in% yrs, ]
out = cbind(round(man,2), round(man$ACL * 0.584, 2), total.catch)

col_names = c("Year", "OFL", "ACL", "OR ACL", "OR Removals")

table_format(x = out,
             caption = "The OFL and ACL for the Minor Nearshore Rockfish North complex, the ACL allocated to Oregon, and the total removals.",
             label = "ofl",
             align = 'l',
             col_names = col_names)


```

\newpage


<!-- ======================================================= -->
<!-- ***************       Data      *********************** --> 
<!-- ======================================================= -->


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/OR_Samples_Feb2021.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/or_rec_samples.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/len_at_age_data.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/len_at_weight_data.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/or_rec_age_samples.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/OR_age_Samples_Feb2021.tex}

\newpage

<!-- ======================================================= -->
<!-- ***************    Biology      *********************** --> 
<!-- ======================================================= -->

```{r, results='asis'}

growth = model$endgrowth[model$endgrowth$Sex == 1, ]
out = growth[, c("Age_Beg", "Len_Beg", "Wt_Beg", "Len_Mat", "Mat*Fecund")]
out$Len_Mat[out$Len_Mat > 0.99] = 1
rownames(out) = NULL
col_names = c('Age', 'Length (cm)', 'Weight (kg)', 'Maturity', 'Spawning Output')

table_format(x = out[1:50,],
             caption = "Age, length, weight, maturity, and spawning output by age (product of maturity and fecundity) at the start of the year. Output for ages 51-90 is truncated as these ages have the same length, weight, maturity, and spawning output as at age 50.",
             label = "growth-tab",
             digits = c(0, 2, 2, 2, 2),
             align = 'l',
             col_names = col_names,
             longtable = TRUE) 

```

\newpage

<!-- ======================================================= -->
<!-- ***************  Data Weights   *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'data_weights.csv'))

col_names = c('Method',
        'Commercial Lengths',
              'Recreational Lengths')
table_format(x = tab,
             caption = "Data weights applied by each alternative data weighting methods. The Dirichlet Multinomial weight is theta/(1+theta)",
             label = "dw",
             align = 'l',
             col_names = col_names)
```

<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}

mod_params = model$parameters[-c(grep('Impl',model$parameters$Label),
							     grep('Fore',model$parameters$Label)),
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 

test = mod_params[which(mod_params$Label == "Wtlen_1_Fem_GP_1"),'Value']
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 

# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')

# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))

# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Fem_GP_1",3]), 3)

# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])

#Reformat so can show a value for alpha in length-weight relationship
mod_params[,"Value"] = format(mod_params$Value, digits = 2)
mod_params[which(mod_params$Label == "Wtlen 1 Fem GP 1"), "Value"] = test

# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')

table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("6cm", "4cm"))                         

```
<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

\include{tex_tables/likelihoods.tex}


<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/TimeSeries.tex}

\newpage

<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->

\include{tex_tables/sensitivities.tex}

\newpage



<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

\input{C:/Users/Brian.Langseth/Desktop/or/write_up/tex_tables/e_ReferencePoints_ES.tex}

\newpage


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'g_Projections_ES.csv'))
man = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")

out = cbind(tab$Year,
            c(man[man$Year %in% c(2021, 2022), "OFL"], rep("-",10)),
            c(man[man$Year %in% c(2021, 2022), "ACL"], rep("-",10)),
            c(round(man[man$Year %in% c(2021, 2022), "ACL"] * 0.584,2), rep("-", 10)),
            c(rep("-",2), round(tab[3:12,2], 2)),
            c(rep("-",2), round(tab[3:12,3],2)),
            c(rep("-",2), round(tab[3:12,3]/tab[3:12,2], 3)),
            round(tab[ ,5:ncol(tab)], 2))

col_names = c('Year',
              'Adopted OFL',
              'Adopted ACL',
              "Adopted ACL-OR",
              "OFL", 
              "ABC", 
              "Buffer",
              "Spawning Output",
              "Fraction Unfished")
table_format(x = out,
             caption = "Projections of potential OFLs (mt), ABCs (mt), estimated spawning output, and fraction unfished. The OFL, ACL, and Oregon (OR) ACL for 2021 and 2022 reflect adopted management limits.",
             label = "project",
             align = 'l',
             col_names = col_names)
```

\newpage

<!--chapter:end:52tables.Rmd-->

\clearpage
# Figures


<!-- ====================================================================== -->  
<!-- ****************** Catches Used in the Model ************************* --> 
<!-- ====================================================================== -->  

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "catch2 landings stacked.png"), 
caption = "Catches by fleet used in the base model",
label = 'catch')
```	


<!-- ====================================================================== --> 
<!-- ******************* Data Used in the Model *************************** --> 
<!-- ====================================================================== --> 

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "data_plot.png"), 
caption = "Summary of data sources used in the base model",
label = 'data-plot')
```	


<!-- ====================================================================== -->
<!-- ****************   Commercial Length Samples    ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_bubflt1mkt0_page2.png"), 
caption = "Length composition data from the commercial fleet",
label = 'com-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_data_weighting_TA1.8_OR_Commercial.png"), 
caption = "Mean length for commercial fleet with 95 percent confidence intervals",
label = 'mean-com-len-data')
```

<!-- ====================================================================== -->
<!-- **************** Recreational Length Samples    ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_bubflt2mkt0_page3.png"), 
caption = "Length composition data from the recreational fleet",
label = 'rec-len-data')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lendat_data_weighting_TA1.8_OR_Recreational.png"), 
caption = "Mean length for recreational fleet with 95 percent confidence intervals",
label = 'mean-rec-len-data')
```

<!-- ====================================================================== -->
<!-- *************************     Biology     **************************** --> 
<!-- ====================================================================== -->


<!-- =================== -->
<!-- ==  Possibly revise  == -->
```{r, results = 'asis'}
add_figure(
filein = file.path(data_fig_loc, "Length_Weight_by_Source.png"), 
caption = "Comparison of the length-at-weight data from the individual sources with length and weight data, and with all sources combined.",
label = 'len-weight-survey')
```	

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio5_weightatsize.png"), 
caption = "Weight-at-length by sex used in the model",
label = 'len-weight')
```	

<!-- =================== -->
<!-- ==  Possibly revise  == -->
```{r, results = 'asis'}
add_figure(
filein = file.path(data_fig_loc, "Length_Age_by_Sex.png"), 
caption = "Observed sex specific length-at-age coastwide data by data source with the estimated length-at-age curve",
label = 'len-age-data')
```	


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio1_sizeatage.png"), 
caption = "Length at age in the beginning of the year in the ending year of the model",
label = 'len-age-ss')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio6_maturity.png"), 
caption = "Maturity as a function of  length",
label = 'maturity')
```


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "bio9_fecundity_len.png"), 
caption = "Fecundity as a function of length",
label = 'fecundity')
```

<!-- =================== -->
<!-- ==  Need to do the following two  == -->

<!-- ```{r, results = 'asis'} -->
<!-- add_figure( -->
<!-- filein = file.path(data_fig_loc, "Length_fraction_female.png"),  -->
<!-- caption = "Fraction female by length across all available data sources", -->
<!-- label = 'len-sex-ratio') -->
<!-- ``` -->

<!-- ```{r, results = 'asis'} -->
<!-- add_figure( -->
<!-- filein = file.path(data_fig_loc, "Age_fraction_female.png"),  -->
<!-- caption = "Fraction female by age across all available data sources", -->
<!-- label = 'age-sex-ratio') -->
<!-- ``` -->


<!-- ====================================================================== -->
<!-- *********************    Selectivity            ********************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "sel01_multiple_fleets_length1.png"),
caption = "Selectivity at length by fleet",
label = 'selex')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts11_Age-0_recruits_(1000s)_with_95_asymptotic_intervals.png"), 
caption = "Estimated time series of age-0 recruits (1000s)",
label = 'recruits')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "recdevs2_withbars.png"), 
caption = "Estimated time series of recruitment deviations",
label = 'rec-devs')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "recruit_fit_bias_adjust.png"),
caption = "Recruitment bias adjustment applied in the base model",
label = 'bias-adj')
```


<!-- ====================================================================== -->
<!-- ****************** Fit to the Length Data **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_residsflt1mkt0_page2.png"), 
caption = "Pearson residuals for commercial fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'com-pearson')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_data_weighting_TA1.8_OR_Commercial.png"), 
caption = "Model estimated mean length (blue line) overlaid on mean length of commercial lengths (gray circles) with 95 percent confidence intervals based on current samples sizes",
label = 'com-mean-len-fit')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_residsflt2mkt0_page3.png"), 
caption = "Pearson residuals for recreational fleet. Closed bubble are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'rec-pearson')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit_data_weighting_TA1.8_OR_Recreational.png"), 
caption = "Model estimated mean length (blue line) overlaid on mean length for recreational lengths (gray circles) with 95 percent confidence intervals based on current samples sizes",
label = 'rec-mean-len-fit')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "comp_lenfit__aggregated_across_time.png"), 
caption = "Aggregated length comps over all years",
label = 'agg-len-fit')
```

<!-- ====================================================================== -->
<!-- ******************      Time Series       **************************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts7_Spawning_output_with_95_asymptotic_intervals_intervals.png"), 
caption = "Estimated time series of spawning output",
label = 'ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts1_Total_biomass_(mt).png"), 
caption = "Estimated time series of total biomass",
label = 'tot-bio')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "ts9_Relative_spawning_output_intervals.png"), 
caption = "Estimated time series of relative spawning output",
label = 'depl')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "UnavailableSpawningOutput.png"),
caption = "Proportion of biomass unavailable due to selectivity for small and large fish.",
label = 'unavail-bio')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "SR_curve.png"), 
caption = "Stock-recruit curve. Point colors indicate year, with warmer colors indicating earlier years and cooler colors in showing later years",
label = 'bh-curve')
```



<!-- ====================================================================== -->
<!-- ******************    Reference Points    **************************** --> 
<!-- ====================================================================== -->


```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "SPR2_minusSPRseries.png"), 
caption = "Estimated 1 - relative spawning ratio (SPR) by year",
label = '1-spr')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(mod_loc, "plots", "yield2_yield_curve_with_refpoints.png"), 
caption = "Equilibrium yield curve for the base case model. Values are based on the 2020
fishery selectivity and with steepness fixed at 0.72",
label = 'yield')
```


<!-- ====================================================================== -->
<!-- ******************       Sensitivity     ***************************** --> 
<!-- ====================================================================== -->

<!-- Need to do plots and model runs  -->

<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- sens_wd = file.path(substr(mod_loc, 1, 50), "_sensitivities", "_plots") -->
<!-- nm = paste0(substr(mod_loc, 52, 99), "_compare2_spawnbio_uncertainty.png") -->
<!-- add_figure( -->
<!-- filein = file.path(sens_wd, nm), -->
<!-- caption = "Change in estimated spawning output by sensitivity", -->
<!-- label = 'sens-ssb') -->
<!-- ``` -->

<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- nm = paste0(substr(mod_loc, 52, 99), "_compare4_Bratio_uncertainty.png") -->
<!-- add_figure( -->
<!-- filein = file.path(sens_wd, nm), -->
<!-- caption = "Change in estimated fraction unfished by sensitivity", -->
<!-- label = 'sens-depl') -->
<!-- ``` -->

<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- nm = paste0(substr(mod_loc, 52, 99), "_compare12_recdevs_uncertainty.png") -->
<!-- add_figure( -->
<!-- filein = file.path(sens_wd, nm), -->
<!-- caption = "Change in estimated annual recruitment deviation", -->
<!-- label = 'sens-recdev') -->
<!-- ``` -->

<!-- ====================================================================== -->
<!-- ******************      Likelihoods      ***************************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_LN(R0)"),  "piner_panel_SR_LN(R0).png"), 
caption = "Change in the negative log-likelihood across a range of log(R0) values",
label = 'r0-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_LN(R0)"),  "SR_LN(R0)_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of log(R0) values",
label = 'r0-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_LN(R0)"),  "SR_LN(R0)_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of log(R0) values",
label = 'r0-depl')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_BH_steep"),  "piner_panel_SR_BH_steep.png"), 
caption = "Change in the negative log-likelihood across a range of steepness values",
label = 'h-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_BH_steep"),  "SR_BH_steep_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of steepness values",
label = 'h-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_SR_BH_steep"),  "SR_BH_steep_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of steepness values",
label = 'h-depl')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_NatM_p_1_Fem_GP_1"),  "piner_panel_NatM_p_1_Fem_GP_1.png"), 
caption = "Change in the negative log-likelihood across a range of female natural mortality values",
label = 'm-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_NatM_p_1_Fem_GP_1"),  "NatM_p_1_Fem_GP_1_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of female natural mortality values",
label = 'm-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_NatM_p_1_Fem_GP_1"),  "NatM_p_1_Fem_GP_1_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of female natural values",
label = 'm-depl')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_L_at_Amax_Fem_GP_1"),  "piner_panel_L_at_Amax_Fem_GP_1.png"), 
caption = "Change in the negative log-likelihood across a range of female maximum length values",
label = 'linf-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_L_at_Amax_Fem_GP_1"),  "L_at_Amax_Fem_GP_1_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of female maximum length values",
label = 'linf-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_L_at_Amax_Fem_GP_1"),  "L_at_Amax_Fem_GP_1_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of female maximum length values",
label = 'linf-depl')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_VonBert_K_Fem_GP_1"),  "piner_panel_VonBert_K_Fem_GP_1.png"), 
caption = "Change in the negative log-likelihood across a range of female k values",
label = 'k-profile')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_VonBert_K_Fem_GP_1"),  "VonBert_K_Fem_GP_1_trajectories_compare1_spawnbio.png"), 
caption = "Change in the estimate of spawning output across a range of female k values",
label = 'k-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_profile_VonBert_K_Fem_GP_1"),  "VonBert_K_Fem_GP_1_trajectories_compare3_Bratio.png"), 
caption = "Change in the estimate of fraction unfished across a range of female k values",
label = 'k-depl')
```


<!-- ====================================================================== -->
<!-- ******************     Retrospectives    ***************************** --> 
<!-- ====================================================================== -->

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_retro"),  "compare2_spawnbio_uncertainty.png"), 
caption = "Change in the estimate of spawning output when the most recent 5 years of data area removed sequentially",
label = 'retro-ssb')
```

```{r, results = 'asis'}
add_figure(
filein = file.path(paste0(mod_loc, "Profile_retro"),  "compare4_Bratio_uncertainty.png"),
caption = "Change in the estimate of fraction unfished when the most recent 5 years of data area removed sequentially",
label = 'retro-depl')
```


\newpage

<!--chapter:end:53figures.Rmd-->

