# Assessment Model

<!-- Summary of Previous Assessments and Bridging analysis -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_model_general.Rmd')
read_child(filein)
```

## Model Structure and Assumptions

`r state` `r spp` was assessed using a one-sex model with life history parameters combined across sexes. The model assumed two fleets: 1) commercial and 2) recreational fleets with removals beginning in `r startyr`. Selectivity for the commercial and recreational fleets was specified to be asymptotic using a six-parameter double normal parameterization. The ascending width and beginning size of maximum selectivity parameters were estimated for each fleet. Annual recruitment deviations were estimated within the base model.

<!-- Modeling Platform and Structure and Priors-->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_model_details.Rmd')
read_child(filein)
```

### Data Weighting

Length composition data for the commercial fishery started with a sample size determined from the equation listed in Section \ref{commercial-fishery} (Table \ref{tab:com-len-samps}). The input sample size for the recreational fishery length composition data was set equal to the number of length samples by year (Table \ref{tab:len-samps}). 

The base model was weighted using the McAllister-Ianelli method, which is based on equation 2.5 and 2.6 in Appendix 2 of McAllister et al. [-@mcallister_bayesian_1997]). The weightings applied using the McAllister-Ianelli method are provided in Table \ref{tab:dw}. This formulation accounts for a lack of independence in sampled fish by downweighting the number of samples. The amount of downweighting for a data set is calculated as the harmonic mean of the effective sample sizes across years. This method does not account for correlation in the data among years. Sensitivities were performed examining the difference in weighting using equation TA1.8 in Francis [-@francis_data_2011] and the Dirichlet Multinomial Weighting (Thorson et al. [-@thorson_model-based_2017]).

### Estimated and Fixed Parameters

There were `r tail(na.omit(model$parameters$Active_Cnt),1)` estimated parameters in the base model. These included one parameter for $R_0$, 4 parameters for selectivity, 81 annual recruitment deviations, and 12 forecast recruitment deviations (Table \ref{tab:params}). 

Fixed parameters in the model were as follows. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`, and natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)`, as described above in Section \ref{priors}. Growth, maturity-at-length, and length-at-weight were fixed as described above in Section \ref{biological-data}. The standard deviation of recruitment deviates was fixed at `r round(model$parameters[model$parameters$Label == "SR_sigmaR","Value"],2)`. Likelihood profiles were performed for steepness, natural mortality, length at maximum size, vonBertalanffy growth coefficient, and the CV at maximum length.

Selectivity in the recreational and commercial fleets was fixed to be asymptotic with only ascending width and beginning size of maximum selectivity being estimated. During initial model development, the descending width and width of maximum selectivity parameters for the recreational and commercial fleets were estimated to identify appropriate fixed values consistent with the data, and then fixed at those estimates. Dome-shaped selectivity was explored for all fleets within the model as sensitivities (see [Sensitivity Analyses](#sensitivity-analyses) section). Older `r spp` are often found in deeper waters and may move into areas that limit their availability to fishing gear. Dome shaped selectivity can also occur under heterogeneous fishing pressure across space by fleets [@Waterhouseetal_spatialSelex_2014]. 

Given the depth closures in the recreational fishery off `r state` it was initially assumed that large `r spp` would not be caught in the fishery indicating dome-shaped selectivity. However, lengths at depth of `r spp` from Remote Operated Vehicle data suggested larger `r spp` occur across depths and are not limited to depths closed to fishing (see [Appendix A](#append_a) for details). This information lead to the assumption of asymptotic selectivity for the recreational fleet for the base model.       

## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, with the goal of estimating a spawning output trajectory for the population of `r spp` off `r state`. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.

