\clearpage
# Tables

<!-- ======================================================= -->
<!-- ***************    Catches      *********************** --> 
<!-- ======================================================= -->

<!-- tab:catch -->
\input{C:/Users/Brian.Langseth/Desktop/ca/write_up/tex_tables/Catches_All_Years.tex}

\newpage

```{r, results = 'asis'}
yrs = hist = 2011:2020
nfleets = 2
catch = dead = total.dead = 0
for (i in 1:nfleets){
  name = paste0("retain(B):_",i)
  input.catch = model$timeseries[model$timeseries$Yr %in% yrs, name]
  catch = cbind(catch, input.catch)
}
total.catch <- round(apply(catch, 1, sum),2)

man_n = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")
man_s = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_south2011_2022.csv")
man_n = man_n[man_n$Year %in% yrs, ]
man_s = man_s[man_s$Year %in% yrs, ]
out = cbind(round(man_n,2), round(man_s[,c("OFL","ACL")],2), round(man_n$ACL * 0.287 + man_s$ACL, 2), total.catch)

col_names = c("Year", "OFL North", "ACL North", "OFL South", "ACL South", "CA ACL", "CA Removals")

table_format(x = out,
             caption = "The OFL and ACL for quillback rockfish within the Minor Nearshore Rockfish North and South complexes, the ACL allocated to California across both complexes, and the total removals.",
             label = "ofl",
             align = 'l',
             col_names = col_names)
```

\newpage

<!-- ======================================================= -->
<!-- ***************       Data      *********************** --> 
<!-- ======================================================= -->


\input{C:/Users/Brian.Langseth/Desktop/ca/write_up/tex_tables/CA_Samples_Feb2021.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/ca/write_up/tex_tables/ca_rec_samples.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/ca/write_up/tex_tables/len_at_weight_data.tex}

\newpage


\input{C:/Users/Brian.Langseth/Desktop/ca/write_up/tex_tables/len_at_age_data.tex}

\newpage



<!-- ======================================================= -->
<!-- ***************    Biology      *********************** --> 
<!-- ======================================================= -->

```{r, results='asis'}

growth = model$endgrowth[model$endgrowth$Sex == 1, ]
out = growth[, c("Age_Beg", "Len_Beg", "Wt_Beg", "Len_Mat", "Mat*Fecund")]
out$Len_Mat[out$Len_Mat > 0.99] = 1
rownames(out) = NULL
col_names = c('Age', 'Length (cm)', 'Weight (kg)', 'Maturity', 'Spawning Output')

table_format(x = out[1:51,],
             caption = "Age, length, weight, maturity, and spawning output by age (product of maturity and fecundity) at the start of the year. Output for ages 51-95 is truncated as these ages have the same length, weight, maturity, and spawning output as at age 50.",
             label = "growth-tab",
             digits = c(0, 2, 2, 2, 2),
             align = 'l',
             col_names = col_names,
             longtable = TRUE) 

```

\newpage

<!-- ======================================================= -->
<!-- ***************  Data Weights   *********************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'data_weights.csv'))

col_names = c('Method',
        'Commercial Lengths',
              'Recreational Lengths')
table_format(x = tab,
             caption = "Data weights applied by each alternative data weighting method. The Dirichlet Multinomial weight is theta/(1+theta)",
             label = "dw",
             align = 'l',
             col_names = col_names)
```


<!-- ======================================================= -->
<!-- ***********   Model Parameters     ******************** --> 
<!-- ======================================================= -->


```{r, results = 'asis'}

mod_params = model$parameters[-c(grep('Impl',model$parameters$Label),
							     grep('Fore',model$parameters$Label)),
                                (names(model$parameters) %in%
                                c("Num","Label","Value","Phase","Min",
                                  "Max","Status","Parm_StDev",
                                  "Pr_type","Prior","Pr_SD"))] 

test = mod_params[which(mod_params$Label == "Wtlen_1_Fem_GP_1"),'Value']
mod_params[,'Value'] = round(as.numeric(mod_params[,'Value']),3)                                 

# Combine bounds into one column
mod_params$Min = paste('(', mod_params$Min, ', ', mod_params$Max, ')', sep='')

# Combine prior info to one column
mod_params$PR_type = ifelse(mod_params$Pr_type == 'No_prior' , 'None', paste(mod_params$Pr_type,' (', mod_params$Prior,  ', ', mod_params$Pr_SD, ')', sep = ''))

# Set long value to scientific notation
mod_params[mod_params$Label == "Wtlen_1_Fem",3] = format(mod_params[mod_params$Label == "Wtlen_1_Fem",3], scientific = TRUE)
mod_params[mod_params$Label == "Eggs_scalar_Fem",3] = format(as.numeric(mod_params[mod_params$Label == "Eggs_scalar_Fem",3]), scientific = TRUE)
mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "L_at_Amax_Fem_GP_1",3]), 4)
mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "VonBert_K_Fem_GP_1",3]), 3)
mod_params[mod_params$Label == "CV_old_Fem_GP_1",3] = round(as.numeric(mod_params[mod_params$Label == "CV_old_Fem_GP_1",3]), 3)

# Remove the max, prior and prior sd columns
drops = c('Max', 'Prior', 'Pr_type', 'Pr_SD', 'Num')
mod_params = mod_params[, !(names(mod_params) %in% drops)]
rownames(mod_params) = c()
mod_params[,"Label"] = gsub("\\_", " ", mod_params[,"Label"])
mod_params[,"PR_type"] = gsub("\\_", " ", mod_params[,"PR_type"])

#Reformat so can show a value for alpha in length-weight relationship
mod_params[,"Value"] = format(mod_params$Value, digits = 2)
mod_params[which(mod_params$Label == "Wtlen 1 Fem GP 1"), "Value"] = test

# Add column names
col_names = c('Parameter',
                         'Value',
                         'Phase',
                         'Bounds',
                         'Status',
                         'SD',
                         'Prior (Exp.Val, SD)')

table_format(x = mod_params,
             caption = "List of parameters used in the base model, including estimated values and standard deviations (SD), bounds (minimum and maximum), estimation phase (negative values not estimated), status (indicates if parameters are near bounds), and prior type information (mean and SD).",
             label = "params",
             align = 'l',
             col_names = col_names,
             longtable = TRUE,
             font_size = 9,
             landscape = TRUE,
             custom_width = TRUE,
             col_to_adjust = c(1,7), 
             width = c("6cm", "4cm"))                         

```

<!-- ======================================================= -->
<!-- ***********    Like Contributions  ******************** --> 
<!-- ======================================================= -->

<!-- tab:likes -->
\include{tex_tables/likelihoods.tex}


<!-- ======================================================= -->
<!-- ***********    Reference Points  ******************** --> 
<!-- ======================================================= -->

<!-- tab:referenceES -->
```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, "tables", "e_ReferencePoints_ES.csv"))
tab = tab[-13,]
col_names = c("", "Estimate", "Lower Interval", "Upper Interval")

tab$Estimate = round(suppressWarnings(as.numeric(tab$Estimate)),2)
tab$Estimate[is.na(tab$Estimate)] = "-"

tab$Lower.Interval = round(suppressWarnings(as.numeric(tab$Lower.Interval)),2)
tab$Lower.Interval[is.na(tab$Lower.Interval)] = "-"

tab$Upper.Interval = round(suppressWarnings(as.numeric(tab$Upper.Interval)),2)
tab$Upper.Interval[is.na(tab$Upper.Interval)] = "-"

table_format(x = data.frame(tab),
                 caption = "Summary of reference points and management quantities, including estimates of
the 95 percent intervals.",
                 label = "referenceES",
                 longtable = TRUE,
                 col_names = col_names,
                 align = c('r','c', 'c', 'c'),
                 row.names = FALSE)

#kableExtra::save_kable(t, file = file.path("C:/Users/Brian.Langseth/Desktop/ca/tex_tables", 
#                                           paste0("e_ReferencePoints_ES", ".tex")))
```


<!-- \input{C:/Users/Brian.Langseth/Desktop/ca/write_up/tex_tables/e_ReferencePoints_ES.tex} -->

\newpage


<!-- ======================================================= -->
<!-- ***********       Time Series      ******************** --> 
<!-- ======================================================= -->

<!-- tab:timeseries -->
\input{C:/Users/Brian.Langseth/Desktop/ca/write_up/tex_tables/TimeSeries.tex}

\newpage

<!-- ======================================================= -->
<!-- ****************     Sensitivities      *************** --> 
<!-- ======================================================= -->

<!-- tab:sensitivities -->
\include{tex_tables/sensitivities.tex}

\newpage



<!-- ======================================================= -->
<!-- ********  Reference Points & Management *************** --> 
<!-- ======================================================= -->

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'g_Projections_ES.csv'))
man_n = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_north2011_2022.csv")
man_s = read.csv("//nwcfile/FRAM/Assessments/CurrentAssessments/DataModerate_2021/Quillback_Rockfish/management/quillback_south2011_2022.csv")

out = cbind(tab$Year,
            c(round(man_s[man_s$Year %in% c(2021, 2022), "OFL"],2), rep("-",10)), 
            c(round(man_s[man_s$Year %in% c(2021, 2022), "ACL"],2), rep("-",10)),
            c(round(man_n[man_n$Year %in% c(2021, 2022), "OFL"],2), rep("-",10)),
            c(round(man_n[man_n$Year %in% c(2021, 2022), "ACL"] * 0.287,2), rep("-",10)),
            c(round(man_n[man_n$Year %in% c(2021, 2022), "ACL"] * 0.287 + man_s[man_s$Year %in% c(2021, 2022), "ACL"],2), rep("-", 10)),
            c(round(tab[1:2,3],2), rep("-",10)),
            c(rep("-",2), round(tab[3:12,2], 2)),
            c(rep("-",2), round(tab[3:12,3],2)),
            c(rep("-",2), round(tab[3:12,3]/tab[3:12,2], 3)),
            round(tab[ ,5:ncol(tab)], 2))

col_names = c('Year',
              'OFL South',
              'ACL South',
              'OFL North',
              'CA ACL North',
              "Total CA ACL",
              "Assumed removals",
              "OFL", 
              "ABC", 
              "Buffer",
              "Spawning Output",
              "Fraction Unfished")
table_format(x = out,
             caption = "Projections of potential OFLs (mt), ABCs (mt), the assumed removals based on 2021 and 2022 adopted ACL values, estimated spawning output, and fraction unfished. The OFL South and ACL South for 2021 and 2022 reflect adopted management limits for quillback rockfish for the area south of 40.10 Latitude N. The OFL North is the year specific total OFL for quillback rockfish, and the CA ACL North is the California specific allocation of the total ACL for 2021 and 2022 north of 40.10 Latitude N. Total CA ACL is the sum of the ACL South and CA ACL North values.",
             label = "project",
             align = 'l',
             col_names = col_names)
```

\newpage

