\clearpage

# Appendix

## Appendix A: Allocation of Yield Among Federal Management Areas{#append_a}

The 2021 California stock assessment for `r spp` represents U.S. waters between the California-Mexico border and the California-Oregon border 42$^\circ$ 00' N. lat. Federal management of the nearshore rockfish complex, that includes `r spp`, is based on areas north and south of 40$^\circ$ 10' N. lat. Therefore, yield estimates from the California base model must be divided between the northern and southern management areas in order to determine the contribution of `r spp` to the nearshore rockfish overfishing limit (OFL). 

Ideally, allocation by area would be based on calculations of habitat by area and/or estimates of biomass by area. Neither of these estimates were available for `r spp` at this time to inform allocations by area. In lieu of this information, historical catches by each region were used to recommend allocation percents by area. Total removals from the recreational and commercial fleets between 2005 - 2020 by areas north and south of 40$^\circ$ 10' N. lat. were calculated. The proportion of removals that are north of 40$^\circ$ 10' N in each year is shown by year in Figure \ref{fig:catch-4010}. During the entire 2005-2020 period, a total of 49.6 percent of all removals were from areas north of 40$^\circ$ 10' N. lat (horizontal dashed line on Figure \ref{fig:catch-4010}) . Based on this, the recommended allocation of the OFLs from the California model be 49.6 percent to the north minor nearshore rockfish complex and 50.4 percent to the south complex. 

```{r, results = 'asis'}
add_figure(
filein = file.path("C:/Users/Brian.Langseth/Desktop/ca", "write_up", "figures", "catch_allocation_4010.png"), 
caption = "Proportion of total removals in the recreational and commercial fisheries that are north of 40 degrees 10 minutes N. lat. by year from 2005 to 2020. The horizontal dashed line is the proportion of total removals over the full 2005-2020 time period that is noth of 40 degrees 10 minutes N. lat",
label = 'catch-4010',
alt_caption = "A dot plot showing proportions between years 2005 and 2020 that vary around 50 percent")
```

\clearpage

## Appendix B: California ROV Survey Data Informing Selectivity{#append_b}

From 2013-2015, the CDFW in collaboration with Marine Applied Research and Exploration (MARE), conducted Remote Operated Vehicle (ROV) surveys along the full length of the California coastline inside MPAs and in reference sites outside for comparison. Density estimates were produced from the ratio of observed fish per unit area observed over the area of seafloor observed by the ROV in fish per meter squared. The percent relative density reflecting the proportion of the density observed in each depth bin was estimated relative to the sum of the density values in observed depths. A particular advantage of ROV data compared to other data sources is the accuracy of the depth of encounter of individual fish, providing useful information regarding selectivity of fishing gear relative to the depth distribution of fish observed by the ROV. Depth restrictions north of Point Conception varied from 20 to 40 fm for most of the last two decades. Densities were highest in the depths of 10 to 50 fm. Therefore, fish occur at depths greater than those that are open to fishing, indicating depth restrictions offer protection of `r spp` biomass (Table \ref{tab:ca-ROV}). 
 
In addition, length frequency distributions by depth were determined from fish observed by the ROV based on visual approximations using the distance between paired lasers. While future efforts to increase the precision of length estimates include using stereo-camera data and programs estimating length from trigonometric calculations, the trends in approximate length distribution with depth still provides useful information. The length frequency distribution by depth is provided in Figure \ref{fig:ca-ROV}. In reviewing both the density by depth and length by depth relative to ontogenetic migration, the patterns may not reflect the smaller fish using shallow rocky reef as juveniles in less than 10 fm, and only reflect the density and composition in deeper depths where ontogenetic migration to deeper depths has already taken place for nearshore species and is not as apparent. 

When examining the length composition data by depth inside and outside of MPAs north of Point Conception (Figure \ref{fig:ca-ROV}), no extreme differences in composition were observed, which is not surprising given the relatively recent implementation of MPAs north of Point Conception between 2007 and 2012. The MPAs make up 20-30% of the rocky reef habitat in state waters within three miles of shore and are intended to preserve the larger individuals as biomass accumulates in MPAs over time. The combination of MPAs and RCAs restrict a larger portion of habitat to fishing (see [Appendix C](#append_c) for details). 

The percentage of fish in 5 cm size categories among 10 fm depths bins north of Point Conception did not show clear signs of increasing size with depth in greater than 10 fm in either region or protected vs. reference sites (Figure \ref{fig:ca-ROV-percent}). This may be in part due to the fish having already moved from shallow kelp forest habitat where the ROV cannot operate to the adult depth distribution in greater than 10 fm by the time they are observed. Only in the shallower depth bins is there higher proportion of smaller individuals. This would indicate that selectivity may not be domed shaped as would be considered if the depth restrictions protected a larger proportion of adult biomass.

```{r, results = 'asis'}
tab = read.csv(file.path(mod_loc, 'tables', 'ca_rov_table.csv'))
tab[2,1] = "10-20"

col_names = c('Depth (fm)',
        'Observed Area (m2)',
        'Quillback Rockfish Observed',
        'Quillback Rockfish Density (fish/m2)',
        'Percent Relative Density')

table_format(x = tab,
             caption = "Counts of fish, areas surveyed by the ROV, density (fish/meter square) and percent relative density by 10 fm depth.",
             label = "ca-ROV",
             align = 'l',
             col_names = col_names)
```

```{r, results = 'asis'}
add_figure(
filein = file.path(appendix_fig_loc, "quillback_rov_lengths.png"), 
caption = "Length frequency distribution in each 10 fm depth bin for quillback rockfish sampled by the ROV in reference locations open to fishing north of Point Conception (above) and State Marine Reserves prohibiting take (below)",
label = 'ca-ROV',
alt_caption = "Two-panel relative frequency stacked bar chart of length counts. Each bar represents a 10 fathom depth bin, and lengths are binned within each bar in 5 cm increments")
```	

```{r, results = 'asis'}
add_figure(
filein = file.path(appendix_fig_loc, "quillback_rov_barchart_length.png"), 
caption = "Percent composition of quillback rockfish length frequency in 5 cm size classes for each 10 fm depth bin from ROV observations north of Point Conception in reference locations where retention is allowed (above) and in State Marine Reserves where retention is prohibited (below)",
label = 'ca-ROV-percent',
alt_caption = "Two-panel three-dimensional bar chart of length counts. Length bins are 5 cm and mulitple groups of bar charts are plotted going into the page and reflect 10 fathom depth categories")
```	

\clearpage

## Appendix C: Percent of Habitat Area Closed to Fishing for Groundfish in the RCAs, CCAs and MPAs in California from 2001-2021{#append_c}

### Introduction
At present, stock assessments reliant on fishery dependent data only represent the areas open to fishing, unless there is a fishery independent data source providing information on the relative abundance and length composition in closed areas. A network of marine protected areas (MPAs) was established between 2003 to 2012 through a regional siting process. The length composition and relative abundance inside and outside MPAs in part results from the presence of MPAs prohibiting take of groundfish established prior to expansion of the current network, duration of existence of new areas, degree of effort prior to protection and criteria for selection focusing on high productivity reefs. These areas are established in perpetuity and will provide substantial protections to nearshore fish stocks for the foreseeable future. 

In addition to MPAs, extensive Rockfish Conservation Areas (RCAs) of varying depths over time and space, as well as the two cowcod conservation areas (CCAs) encompassing 4200 square miles of water area since 2001, were established to facilitate rebuilding of overfished species.  While the depth restrictions in these closed areas can change or be eliminated, the areas closed become refugia that reduce fishing mortality, allowing accumulation of biomass within them. There has long been interest in quantifying the area of reef habitat for each assessed species that resides in protected areas, but until very recently, there was insufficient data on the distribution of rocky reef habitat. This analysis provides the percentage of habitat area for copper and quillback rockfish closed to fishing in MPAs, RCAs and CCAs where the take of groundfish was prohibited in each year from 2001 to 2021. 

 
### Methods
#### Descriptions of the habitat layers 
A predictive substrate layer that identifies hard and soft substrate was used to analyze seafloor coverage within the 3 nautical miles from California’s shore. Substrate types were generated algorithmically using rugosity analysis, to identify areas likely to have rocky reefs. This layer was derived from bathymetric data of 2, 5 and 10 m resolution and bathymetric data were collected by California Seafloor Mapping Project (CSMP). Potential issues with this rugosity analysis include noise and artifacts resulting from unusual substrate structure, original mapping data, and steep slopes. In addition, hard substrate might be underestimated in areas with canyon slopes, deep water, over smooth rock and where sediments cover rock. 

Data from the CSMP is known to have nearshore data gaps referred to as the white zone. Contributors from The University of California Santa Cruz, California Ocean Science Trust, and California Department of Fish and Wildlife (CDFW) conducted a 30 m resolution interpolation analysis to estimate hard and soft substrate within the white zone. The interpolation analysis utilized data from the CSMP and National Oceanic and the National Oceanic and Atmospheric Administration Environmental Sensitivity Index (ESI). Accuracy of the interpolation is estimated to be best where the white zone bands are narrowest and worst where the white zone bands are widest. In addition, metadata indicates the interpolation is questionable at scales finer than 100 m.

Substrate data developed for an Essential Fish Habitat Review was incorporated into this analysis for seafloor occurring outside of California State Waters (3 nautical miles). This dataset was generated by Joe Bizarro of the National Marine Fisheries Service, Southwest Fisheries Science Center in Santa Cruz and was created by combining multiple sources of bathymetric data with varying resolutions including multibeam sonar, sidescan sonar, sediment grabs, core samples seismic reflection profiles, still photos and video. This habitat data is subject to georeferencing errors and data resolution errors. Currently this is the best available data that represents hard and soft substrate types offshore for the areas outside of California State waters. 

#### Boundaries of the CCAs, RCAs and MPAs 
Regulation histories for each type of closure were converted to Boolean fields with zeros and ones indicating absence and implementation, respectively from 2001-2020. The corresponding GIS layers were either available from previous CDFW GIS staff projects or approximated by the depth contour where specific weigh points were unavailable. The area in MPAs prohibiting take by the recreational and commercial fisheries were included in the estimates of area closed to fishing from the first year in which the MPA was in place for a full calendar year. The Western CCA area accounted for waters around islands and banks open to take of a limited suite of groundfish species including copper rockfish. The RCAs for commercial and recreational fisheries were based on the deeper of the depth restrictions for the sectors to reflect only areas where take was prohibited for both. Where the RCA lines for the stock in question were not available, depth contours were used to approximate the percent of area closed. 

#### Delineating Habitat in Restricted Areas and Open to Fishing
The depth range of habitat for copper and quillback rockfish was between shore to 100 m, covering the primary depth distribution of both stocks observed in the CDFW ROV survey (Budrick et al. -@Budricketal_rov_2019) or noted in Love et al. -@loveetal_2002). The latitudinal range was set from the California/Mexican border to the California/Oregon border (42$^\circ$ N. lat.), which was stratified north and south Point Conception (34$^\circ$ 27’ N. lat.). Quillback rockfish are relatively rare south of Point Conception, thus only estimates for the area north of Point Conception are pertinent to this stock. 
 
The distribution and area of rocky reef habitat within a species range was delineated in ArcGIS Pro (2.6) by extracting specific values from a 10 m bathymetric raster based on species depth and latitudinal ranges. The resulting raster layer was converted into a shapefile and merged with a coastal boundary of California to account for gaps in the bathymetric raster. Hard habitat within the species range was identified and isolated using the intersect tool to create species range shapefile. This process was repeated to identify overlapping coverage between the species range and hard substrate, as well as intersecting the species range with a combination of different types of regulatory boundaries. 

The area of the resulting shapefiles were calculated in GIS and exported into tables using Python script. The combination of area closures in a given year were overlayed on the habitat maps, with the area in MPAs and CCAs extracted first, then the habitat in the remaining RCAs estimated. The residual habitat still open to fishing after accounting for the closed areas was then estimated. The area of rocky reef habitat closed to fishing within a species range was converted to a percentage of the total habitat. This process for identifying overlapping boundaries and calculating areas were scripted in Python to reduce the possibility of human error. 

#### Examination of bottom type coverage relative to habitat 
The extent of existing substrate data within a given species range was examined through geospatial analysis. This included hard, soft, and unknown substrate for data from California Seafloor Mapping Project, and hard, mixed, and soft data from the EFH project. Both datasets were merged within the species range for copper and quillback rockfish. The resulting combination of substrate data was erased from the species range. 
 
### Results
The tables reflecting the percent of habitat area in RCAs, MPAs, CCAs closed to fishing for groundfish and waters open to fishing are provided for north of Point Conception (Table \ref{tab:ca-mpa}). The potential habitat within the primary depth range of the species, rocky reef habitat within the potential habitat, MPAs and CCAs are depicted for the entire state (Figure \ref{fig:ca-mpa-map}). 

We found minimal voids in coverage in habitat layers across the species range, with 0.13 square miles missing north of Point Conception and 4.95 square miles missing from the south of Point Conception. 

### Discussion
Current assessments do not account for length/age composition and differing fishing mortality rates inside and outside MPAs or waters in long-established CCAs and RCAs. As biomass accrues inside these areas, accounting for protections through area-based assessment methods or effects on selectivity should be considered as fishery dependent data will only reflect the length composition and density outside. There is the potential for future assessments to account for differences in length composition, fishing mortality and relative abundance in a two-area model in Stock Synthesis with available data from long-term MPA monitoring.  

Additional high resolution side scan sonar data in waters seaward of the CSMP coverage would improve coverage and resolution of habitat data. Similar analyses for each nearshore or shallower distributed shelf rockfish species (i.e. vermilion rockfish) would be a helpful addition to stock assessments to inform time blocking and selectivity considerations. The extent and design of the network to function in this way is unique to California and it’s efforts to conserve nearshore stocks. Until the closed areas can be accounted for explicitly in stock assessments, the substantial areas in MPAs should be taken into consideration as a buffer against overfishing, since they were established in the interest of preserving spawning stock to seed areas outside and other MPAs in the network.  
 

```{r, results = 'asis'}
tab = read.csv(file.path("L:/Assessments/CurrentAssessments/DataModerate_2021/Data_From_States/ca", 'Percent Habitat Area in MPA-RCA-Open to Fishing for Copper and Quillback North of Conception_finalized_June202021.csv'))

col_names = c('Year',
        'Percent Habitat Protected by MPA',
        'Percent Habitat Protected by RCA',
        'Percent Habitat Open to Fishing')

table_format(x = tab,
             caption = "Percent of rocky reef habitat protected for quillback and copper rockfish north or Point Conception by MPAs and RCAs, and the total percent habitat open to fishing.",
             label = "ca-mpa",
             align = 'l',
             col_names = col_names,
             row.names = FALSE)
```
\clearpage

```{r, results = 'asis'}
add_figure(
filein = file.path(appendix_fig_loc, "ca_mpa_rca_habitat_map.png"), 
caption = "Copper and quillback rockfish potential depth range off California in red hatched polygon, hard substrate occurring within the potential range in pink, MPAs in dark blue outline, and the CCAs in light blue",
label = 'ca-mpa-map',
alt_caption = "Bathymetric map of the California coast highlighting locations of hard substrate and potential rockfish habitat, with insets showing areas near Monterey Bay, Cape Mendocino, and the Channel Islands")
```

\clearpage

## Appendix D: Detailed Fit to Annual Length Composition Data{#append_d}


```{r, results='asis'}
plot_info = read.csv(file.path("C:/Users/Brian.Langseth/Desktop/ca/7_1_1_base_ghostCom", "plots", "plotinfotable_for_doc.csv"))
len_fit = plot_info[which(plot_info$category == "LenComp"), ]
plot.vec = c(grep("comp_lenfit_flt", len_fit$label),grep("comp_gstlenfit_flt", len_fit$label))
filein = file.path("C:/Users/Brian.Langseth/Desktop/ca/7_1_1_base_ghostCom", "plots")
altcap = list()

for (a in plot.vec){
	cap = sub("[.]$", "", len_fit$caption[a])
	lab = len_fit$label[a]
	add_figure(filein = file.path(filein, len_fit$file[a]), 
			   caption = cap, 
			   label = lab,
			   alt_caption = "Multi-panel density plot showing length distributions by year along with a line showing the model fit. Each panel represents a separate year")
}
```


\clearpage

