# Assessment Model

<!-- Summary of Previous Assessments and Bridging analysis -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_model_general.Rmd')
read_child(filein)
```


## Model Structure and Assumptions

`r state` `r spp` was assessed using a one-sex model with life history parameters combined across sexes. The model assumed two fleets: 1) commercial and 2) recreational fleets with removals beginning in `r startyr`. Selectivity for the commercial fleet was specified to be asymptotic using the six-parameter double normal parameterization within Stock Synthesis. The ascending width and beginning size of maximum selectivity parameters were estimated for the commercial fleet. The selectivity for the recreational fleet was also specified using the six-parameter double normal parameterization with the ascending width and beginning size of maximum selectivity parameters estimated, and reduced selectivity for the largest fish was allowed (i.e., allowed to be dome-shaped). Annual recruitment deviations were estimated within the base model.

<!-- Modeling Platform and Structure and Priors and Data Weighting -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_model_details.Rmd')
read_child(filein)
```

<!-- Data Weighting -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '3_data_weighting.Rmd')
read_child(filein)
```

### Estimated and Fixed Parameters

There were `r tail(model$parameters$Active_Cnt,1)` estimated parameters in the base model. These included one parameter for $R_0$, 5 parameters for selectivity, 71 annual recruitment deviations, and 12 forecast recruitment deviations (Table \ref{tab:params}).

Fixed parameters in the model were as follows. Steepness was fixed at `r round(model$parameters[model$parameters$Label == "SR_BH_steep","Value"],2)`, and natural mortality was fixed at `r round(model$parameters[model$parameters$Label == "NatM_p_1_Fem_GP_1","Value"],3)`, as described above in Section \ref{priors}. Growth, maturity-at-length, and length-at-weight were fixed as described above in Section \ref{biological-data}. The standard deviation of recruitment deviates was fixed at `r round(model$parameters[model$parameters$Label == "SR_sigmaR","Value"],2)`. Sensitivity analyses and likelihood profiles were performed for steepness, natural mortality, length at maximum size, and vonBertalanffy growth coefficient. 

Dome-shaped selectivity was explored for all fleets within the model. Older and larger `r spp` may be found in deeper waters and may move into areas that limit their availability to fishing gear as they mature. Dome shaped selectivity can also occur under heterogeneous fishing pressure across space by fleets [@Waterhouseetal_spatialSelex_2014].

The final base model estimated dome-shaped selectivity for the recreational fishery. The selectivty for the commercial fishery was fixed as asymptotic. During initial model development, the descending width and width of maximum selectivity parameters for the recreational and commercial fleets were estimated to identify appropriate fixed values consistent with the data, and then fixed at those estimates. 


## Model Selection and Evaluation

The base assessment model for `r spp` was developed to balance parsimony and realism, and the goal was to estimate a spawning output trajectory for the population of `r spp` off the `r coast` coast. The model contains many assumptions to achieve parsimony and uses many different sources of data to estimate reality. A series of investigative model runs were done to achieve the final base model.

