# Introduction

## Basic Information

This assessment reports the status of `r spp` (*`r spp_latin`*) off the `r state` coast using data through `r endyr`. 

The stock off the `r state` coast was assessed as a separate stock from other populations off the U.S. West Coast based on two factors. First, the fairly sedentary nature of `r spp` [@HannahandRankin_rockfish_site_fidelity_2011; @tolimieri_home_2009] likely limits movement of fish between Washington and Oregon. Additionally, the primary region of recreational fishing off the Washington coast occurs in the central to northern regions. These areas have rocky habitat with which rockfish species such as `r spp` associate. In contrast the southern coast of Washington consists primarily of soft and sandy substrate. Second, the exploitation history and magnitude of removals off the `r state` coast differ from those in Oregon and California.    

<!-- Life history -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '1_introduction_basic_life_ecosystem.Rmd')
read_child(filein)
```

## Historical and Current Fishery Information

Off the Washington coast, `r spp` is primarily caught in the recreational fishery, and in general, is not targeted by either commercial or recreational fleets (Table \ref{tab:allcatches} and Figure \ref{fig:catch}). Recreational landings of `r spp` were provided by the Washington Department of Fish and Wildlife (WDFW) and for most years were available from 1958 to present, with a linear interpolation applied for years where data were missing. Recreational harvest is focused in the central and northern regions in areas of rocky habitat. Although populations are considered to be widespread in the nearshore marine environment, abundance may be limited along the southern coast which consists primarily of soft and sandy substrate. 

Commercial landings data are available from the WDFW historical reconstruction prior to 1981 and from PacFIN from 1981 through 2020. Washington state waters, which mostly encompass the depths preferred by `r spp`, were closed to commercial fixed gears in 1995 and to trawling in 1999. In response to the development of the live-fish fishery in California and Oregon, Washington took preemptive action in 1999 by prohibiting the landing of live fish. There are four treaty tribes along the Washington coast that continue to fish under separate commercial rules and are not subject to the state water closure. These tribes occasionally land small amounts of `r spp`. `r Spp` are usually landed in the Nearshore Rockfish group, a mixed-species market category. Species composition samples are taken from sampled landings, and proportions of `r spp` reported in the nearshore market category are estimated by port, quarter, gear, and year.

<!-- Summary of Management History and Performance -->

```{r, echo=FALSE, results='asis'}
general_wd = "U:/Stock assessments/quillback_rockfish_2021/write_up/general_text"
filein = file.path(general_wd, '1_introduction_management.Rmd')
read_child(filein)
```

The current OFL contribution and implied ACL contribution for `r spp` North of 40$^\circ$ 10' Lat. N., the state specific ACL allocation (12.9% for `r state`; Groundfish Management Team, pers. comm.), and the total removals are shown in Table \ref{tab:ofl}.
