---
title: "Quillback Rockfish: Responses to Additional Requests From the Groundfish Subcommittee for the California Model"
author: "Brian J. Langseth"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
bibliography: postSSC.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(sa4ss)
library(tidyr)
data_dir = "L:\\Assessments\\CurrentAssessments\\DataModerate_2021\\Quillback_Rockfish\\data\\forSS"
mod_dir = "C:\\Users\\Brian.Langseth\\Desktop\\ca"
```

# Requests Based on Additional or Adjusted Data

## Request 2: 

Add the length data from the historical onboard CPFV surveys from the 1980s and 1990s northern California survey conducted by CDFW noted in Table 2 of the SSC Report.

Rationale: While the CRFS and MRFSS data may provide consistent sampling over time and space, the sample sizes for lengths from the MRFSS era are relatively low due to low sampling frequency and only sampling 30 anglers per day.  Addition of these supplementary data sources will help increase the sample size providing more insight on the effects of the low sample size.

## Response 2:

Additional length data for quillback rockfish were provided by California Department of Fish and Wildlife (CDFW) on July 12, 2021. These data were collected by observers onboard commercial passenger fishing vessels (CPFV) fishing in central California (@Reilly1998) from 1987-1998, and were not available for use in the base model that was reviewed and adopted in the June Groundfish Subcommittee meeting of the Scientific
and Statistical Committee (GFS-SSC). A total of 753 additional length observations for the recreational fleet from 1987-1998 (Table \ref{tab:len_data}) were added to the California quillback rockfish base model.

Length distributions from the new data were generally similar to existing length distributions within the adopted base model (Figure \ref{fig:sens-debWV-comp}). Given the use of new data, scenarios with and without data weighting were run. Changes to data weights were minimal and resulted in little change in model trajectories. Spawning output (Figure \ref{fig:sens-debWV-ssb}), depletion (Figure \ref{fig:sens-debWV-depl}), and recruitment deviations (Figure \ref{fig:sens-debWV-rdevs}) from models with the new data were similar to those from the adopted base model. Adding the new length data resulted in lower estimates of initial spawning output (SB virgin) and recent spawning output (SB2021) compared to the adopted base model, and resulted in a slightly more depleted stock. Parameter estimates, derived quantities, and likelihood components for each scenario are provided in Table \ref{tab:sens-table}. Given that different datasets were used for the scenarios, likelihood and AIC values cannot be compared to the adopted base model. 

```{r data_table, results = 'asis', echo = FALSE} 

deb  <- read.csv(file.path(data_dir,"ca_rec_samples_debWV.csv"), header = TRUE)
orig  <- read.csv(file.path(data_dir,"ca_rec_samples.csv"), header = TRUE)
ldat <- merge(deb[,1:2], orig[,1:2], by = "Year", all = TRUE)

ldat[is.na(ldat)] <- "-"

col_names <- c("Year", "New lengths", "Original lengths")
table_format(x = ldat[ldat$Year %in% c(1987:1998),],
             caption = "Number of additional length samples by year (new lengths) from 1987-1998 for quillback rockfish onboard CPFVs in central California as provided by CDFW. The number of length samples in the base model (original lengths) is provided for comparison.",
             label = "len_data",
             align = 'l',
             row.names = FALSE,
             col.names = col_names)
```

```{r, results = 'asis', echo = FALSE}
add_figure(
filein = file.path("C:/Users/Brian.Langseth/Desktop/ca", "postSSC_plots", "ForReport", "Comp_overlap.png"),
caption = "Length distributions of the new data (red line) compared to the original data (blue line) in years where the new data were available (1987-1998). Numbers indicate the number of lengths from each dataset for each year that are also shown in Table 1",
label = 'sens-debWV-comp')
```

```{r, results = 'asis', echo = FALSE}
add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "base.800_debWV_sensitivities_compare2_spawnbio_uncertainty.png"), 
caption = "Change in estimated spawning output across scenarios when adding 1987-1998 central California CPFV length data. Shading indicates 95% confidence intervals around each scenario",
label = 'sens-debWV-ssb')

add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "base.800_debWV_sensitivities_compare4_Bratio_uncertainty.png"), 
caption = "Change in estimated fraction of unfished across scenarios when adding 1987-1998 central California CPFV length data. Shading indicates 95% confidence intervals around each scenario",
label = 'sens-debWV-depl')

add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "base.800_debWV_sensitivities_compare12_recdevs_uncertainty.png"), 
caption = "Yearly recruitment deviations (points) across scenarios when adding 1987-1998 central California CPFV length data. Vertical lines represent the 95% confidence intervals of the deviations for each scenario",
label = 'sens-debWV-rdevs')
```

\newpage

## Request 3:  

Reevaluate the catch history taking into account input from the CDFW Report 1 and Report 2 as well as input from the California STAT member to address apparent outlier estimates and methods for filling blanks between 1990 and 1992 for the MRFSS era.

Rationale:  The CDFW reports identify a number of historical catch reconstruction considerations that appear to be outliers that affect depletion and scale.  This request is intended to evaluate the effects of their inclusion on the assessment and reconsider the basis for their inclusion.

## Response 3:

No new catch values were provided by CDFW for inclusion in this document. As such, no additional explorations were conducted. 

An alternative catch history was previously explored in the original [California quillback rockfish report](https://www.pcouncil.org/documents/2021/06/g-5-attachment-10-draft-status-of-quillback-rockfish-sebastes-maliger-in-u-s-waters-off-the-coast-of-california-in-2021-using-catch-and-length-data-electronic-only.pdf/) (see sensitivity #14 on page 18 of that report). The average catch in the three years before and three years after years with high catch were used in the alternative catch time series. Catch was higher than neighboring years in 1991 for the commercial fleet, and 1983 and 1993 for the recreational fleet. Alternative catch values were therefore applied to these years. Reducing the magnitude of catch resulted in lower estimates of initial and recent spawning output compared to the adopted base model, and resulted in a slightly more depleted stock. For detailed results of this sensitivity, see Table 13, and Figures 47-49 from the [California quillback rockfish report](https://www.pcouncil.org/documents/2021/06/g-5-attachment-10-draft-status-of-quillback-rockfish-sebastes-maliger-in-u-s-waters-off-the-coast-of-california-in-2021-using-catch-and-length-data-electronic-only.pdf/).  



## Request 5: 

Age otoliths and use corresponding lengths from samples collected in California and compare results to the growth curve from samples collected in Oregon and Washington. Otoliths should be provided as requested in the NMFS Report 1 (Agenda Item C.10, Supplemental NMFS Report 1, June 2021).

Rationale:  Comparison of ages and lengths of fish sampled in California to the growth curve derived from samples collected in Oregon and Washington will provide a means of examining whether the growth curve provided by them are representative of growth in California. 

## Response 5:

CDFW provided otoliths from 35 quillback rockfish collected from the commercial (N = 6) and recreational (N = 29) fisheries, sampled nearly exclusively from Crescent City, California. In addition, 44 otoliths from CCFRP sampling were provided. An additional 39 otoliths from port sampling efforts were provided by Southwest Fisheries Science Center staff, as were 123 otoliths from the Abrams collection housed at the Southwest Fisheries Science Center. Tables for the number of new otoliths by year (Table \ref{tab:age-year}) and by length bins (Table \ref{tab:age-bins}) are provided.

```{r, echo = FALSE}
agelen <- read.csv("L:\\Assessments\\CurrentAssessments\\DataModerate_2021\\Quillback_Rockfish\\data\\postSSC_request_data\\combined_age_metadata.csv", header = TRUE)
agelen$length_cm = agelen$FL..mm./10
agelen$bins = 2 * floor(agelen$length_cm/2)
#By year
agelen_year <- aggregate(length_cm ~ Year + Source, data = agelen, length)
agelen_year_wide <- spread(agelen_year, Source, length_cm)
agelen_year_wide[is.na(agelen_year_wide)] <- 0
#By bin
agelen_bin <- aggregate(length_cm ~ bins + Source, data = agelen, length)
agelen_bin_wide <- spread(agelen_bin, Source, length_cm)
agelen_bin_wide[is.na(agelen_bin_wide)] <- 0

colnames_year <- c("Year", "Abrams", "CDFW Comm.", "CDFW Rec.", "SWFSC boxes", "SWFSC trays")

tyear = table_format(x = agelen_year_wide,
                 caption = 'Number of new otoliths available by year and source.',
                 label = 'age-year',
                 longtable = TRUE,
                 font_size = 9,
                 col_names = colnames_year)

kableExtra::save_kable(tyear, file = file.path("U:\\Stock assessments\\quillback_rockfish_2021\\write_up\\postSSC_responses", "age_year_table.tex"))

colnames_bins <- c("Length bins (cm)", "Abrams", "CDFW Comm.", "CDFW Rec.", "SWFSC boxes", "SWFSC trays")

tbin = table_format(x = agelen_bin_wide,
                 caption = 'Number of new otoliths available by length bin and source. Structures are not available for all modeled length bins',
                 label = 'age-bins',
                 longtable = TRUE,
                 font_size = 9,
                 col_names = colnames_bins)

kableExtra::save_kable(tbin, file = file.path("U:\\Stock assessments\\quillback_rockfish_2021\\write_up\\postSSC_responses", "age_bins_table.tex"))
```

\newpage

<!-- tab:sensitivities -->
\input{U:/Stock assessments/quillback_rockfish_2021/write_up/postSSC_responses/age_year_table.tex}

<!-- tab:sensitivities -->
\input{U:/Stock assessments/quillback_rockfish_2021/write_up/postSSC_responses/age_bins_table.tex}


<!-- New samples were used to compare a California growth curve from new data only with the growth curve used in the quillback rockfish assessments, which included 21 ages from the WCGBTS collected in California waters. Given the use of some California data from the WCGBTS in the assessments, we also compared a growth curve with the 21 ages from the WCGBTS in California combined with thew new california data to that of only Oregon/Washington data.  -->

Otoliths were sent to the Northwest Fisheries Science Center's ageing lab in Newport, Oregon. Complete results were not available at the time of submitting this report.   


\newpage




# Requests Based on Additional Model Runs


## Request 1: 

Evaluate alternative selectivity time blocking based on the timing of depth restrictions from 2001-present north of Pigeon Point, California where they are commonly encountered. In particular add a time block (allowing for dome-shaped selectivity) starting in 2001 and consider additional time blocks. 

Rationale:  Input from the GAP and GMT indicate that asymptotic selectivity for the recreational fishery is not a realistic assumption and was made to fit the need for the model to have at least one sector be asymptotic as required by the TOR (pg 36) . It seems more realistic to consider the period before severe regulations in the early 2000s as asymptotic (or domed) and then consider domed shape assumptions thereafter, perhaps with a separate dome shape after 2016 when regulations were slightly relaxed. 

## Response 1:

Alternative selectivity forms and blocks were explored during original model explorations. The choice of using asymptotic selectivity for the recreational fleet was based on findings from ROV surveys conducted by CDFW that did not show clear signs of increasing size with depth at depths greater than 10 fm. Assuming dome-shaped selectivity also resulted in a similar trajectory as when assuming asymptotic selectivity. Consequently, there was limited support for the additional complexity when adding parameters due to blocking of selectivity. Additional runs here also show limited support for the additional complexity in blocking selectivity. 

We explored numerous options for blocking selectivity based on changes in the estimated percent of area open to fishing (Table A-1 from [CDFW Report 1](https://www.pcouncil.org/documents/2021/06/g-5-a-supplemental-cdfw-report-1.pdf/)), as well as changes in mean length from the length data in the adopted base model (Figure 20 from the California quillback rockfish report). Specific blocking along with the reasons for blocking (in parenthesis) are described below. In all instances, the model was allowed to estimate dome-shaped selectivity by estimating selectivity parameters controlling the peak size of selectivity (parameter 1), the width of the peak (parameters 2), the width of the ascending and descending limbs of selectivity (parameters 3 and 4), and the selectivity for large individuals (parameter 6). 

\begin{enumerate}
   
  \item Blocking selectivity from 1916-2000 assuming asymptotic selectivity, and 2001-2020 allowing for dome-shaped selectivity (as requested).
  
  \item Blocking selectivity from 1916-2000 assuming asymptotic selectivity, 2001-2016 allowing for dome-shaped selectivity, and 2017-2020 allowing for dome-shaped selectivity (due to depth restrictions starting in 2001 and a relaxation of those restrictions starting in 2017).
  
  \item Blocking selectivity from 1916-2000 assuming asymptotic selectivity, 2001-2002 allowing for dome-shaped selectivity, 2003-2007 allowing for dome-shaped selectivity, 2008-2016 allowing for dome-shaped selectivity, and 2017-2020 allowing for dome-shaped selectivity (due to depth restrictions starting in 2001, changes in the percent of area open to fishing in 2003 and again in 2008, and a relaxation of depth restrictions starting in 2017).
  
  \item Blocking selectivity from 1916-2000 assuming asymptotic selectivity, 2001-2004 allowing for dome-shaped selectivity, and 2005-2020 allowing for dome-shaped selectivity (due to depth restrictions starting in 2001, and a noticeable change in mean length in 2005).
  
  \item Blocking selectivity from 1916-2000 assuming asymptotic selectivity, 2001-2004 allowing for dome-shaped selectivity, 2005-2016 allowing for dome-shaped selectivity, and 2017-2020 allowing for dome-shaped selectivity (due to depth restrictions starting in 2001, a noticeable change in mean length in 2005, and a relaxation of depth restrictions starting in 2017).
  
  \item Blocking selectivity as in option 1 above, but with the new length data from request 3 in the model.
         
\end{enumerate}

Data weights were not reweighted for any of the selectivities from this request, in keeping with typical practices when running sensitivities. Suggested reweighting values were within 5% of the original weights from the adopted base model. Under option 2, the selectivity parameter (parameter 2) controlling the width of the peak hit its lower bound, which was resolved by fixing this parameter at its lower bound.  

The additional options explored here show limited support for the additional complexity in blocking selectivity. Spawning output (Figure \ref{fig:sens-block-ssb}) and depletion (Figure \ref{fig:sens-block-depl}) from models with alternative blocking for the recreational fleet were similar to those from the adopted base model. Adding selectivity blocks with the flexibility for dome-shaped selectivity resulted in slightly larger estimates of initial spawning output (SB virgin) and recent spawning output (SB2021) compared to the adopted base model, and resulted in a slightly less depleted stock. 

Selectivity of the recreational fleet for each scenario is shown in Figure \ref{fig:sens-block-selex}. Other parameter estimates, derived quantities, and likelihood components for each scenario are provided in Table \ref{tab:sens-table}. The added parameter flexibility resulted in improved fits to length compositions, but AIC was improved by more than 2 units for only one option (option 2). Pearson residuals (Figure \ref{fig:Pearson-block}) were visually similar among scenarios as were fits to mean lengths (Figure \ref{fig:MeanLengthFit-block}) with only slight changes occurring in the year between blocks. The scenario with both blocking and new data added is not shown in Figures \ref{fig:Pearson-block} and \ref{fig:MeanLengthFit-block} for ease of comparisons.

```{r, results = 'asis', echo = FALSE}
add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "base.800_block_sensitivities_compare2_spawnbio_uncertainty.png"), 
caption = "Change in estimated spawning output across scenarios for blocking selectivity in the recreational fleet. Shading indicates 95% confidence intervals around each scenario",
label = 'sens-block-ssb')

add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "base.800_block_sensitivities_compare4_Bratio_uncertainty.png"), 
caption = "Change in estimated fraction of unfished across scenarios for blocking selectivity in the recreational fleet. Shading indicates 95% confidence intervals around each scenario",
label = 'sens-block-depl')
```

```{r, results = 'asis', echo = FALSE}
add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "Selex_together.png"), 
caption = "Recreational selectivity across scenarios for blocking the recreational fleet",
label = 'sens-block-selex')
```

```{r, results = 'asis', echo = FALSE}
add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "Pearson_block.png"), 
caption = "Pearson residuals for the recreational fleet across options of blocking selectivity. Closed bubbles are positive residuals (observed > expected) and open bubbles are negative residuals (observed < expected)",
label = 'Pearson-block',
width = 90, height = 90)

add_figure(
filein = file.path(mod_dir, "postSSC_plots", "ForReport", "MeanLengthFit_block.png"), 
caption = "Mean length and fit (green line) for the recreational length data with 95% confidence intervals (solid black bar) based on current samples sizes. Thinner intervals (with capped ends) show result of further adjusting sample sizes based on suggested multiplier for Francis data weighting",
label = 'MeanLengthFit-block',
width = 90, height = 90)
```

\newpage

## Request 4: 

Further evaluate the ability of the model to estimate growth. In particular, run one model while estimating L-infinity and another while estimating both L-infinity and k.

Rationale: The current model uses estimates of growth from fish collected in Oregon and Washington.  Given the higher water temperatures in California, this request is for examination of the ability of the model to estimate growth given the sensitivity of the model and the apparent information in lengths to inform them as seen in profiles of L infinity and k, while, admittedly, estimating k without age data may be problematic.

## Response 4:

The two requested runs were completed in the original [California quillback rockfish report](https://www.pcouncil.org/documents/2021/06/g-5-attachment-10-draft-status-of-quillback-rockfish-sebastes-maliger-in-u-s-waters-off-the-coast-of-california-in-2021-using-catch-and-length-data-electronic-only.pdf/) (sensitivities #4 and #6 on page 17 of that report). Estimating growth parameters resulted in similar estimates of initial spawning output and larger estimates of recent spawning output compared to the adopted base model, and consequently resulted in a less depleted stock. Detailed results for these sensitivities are shown in Table 13 and Figures 47-49 in the [California quillback rockfish report](https://www.pcouncil.org/documents/2021/06/g-5-attachment-10-draft-status-of-quillback-rockfish-sebastes-maliger-in-u-s-waters-off-the-coast-of-california-in-2021-using-catch-and-length-data-electronic-only.pdf/) and are not repeated here.   


<!-- tab:sensitivities -->
\input{C:/Users/Brian.Langseth/Desktop/ca/postSSC_plots/ForReport/sensitivities.tex}
\input{C:/Users/Brian.Langseth/Desktop/ca/postSSC_plots/ForReport/sensitivities_withComBlock.tex}


# References
<!-- If you want to references to appear somewhere before the end, add: -->
<div id="refs"></div>

